### 2024-02-12 outputs/paper/paper.qmd
Updates to paper

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - First author
  - Another author
thanks: "Code and data are available at: LINK."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)

cleaned_data <- read_csv(here::here("outputs/Data/analysis_data.csv"))

```

# Introduction

The introduction is self-contained and tells a reader everything they need to know including: 1) broader context to motivate; 2) some detail about what the paper is about; 3) a clear gap that needs to be filled; 4) what was done; 5) what was found; 6) why it is important; 7) the structure of the paper. A reader should be able to read only the introduction and know what was done, why, and what was found. Likely 3 or 4 paragraphs, or 10 per cent of total.

You can and should cross-reference sections and sub-sections.

The remainder of this paper is structured as follows. @sec-data....

# Data {#sec-data}

The data used in this paper is from (cite og paper). The data used in the paper is extremely compplicated as it combines numerous data sets to complete their analysis. In this paper, we wanted to simplify the data 
```{r}

ggplot(cleaned_data, aes(x = reorder(hhld_inc, -table(hhld_inc)[hhld_inc]), fill = hhld_inc)) +
  geom_bar() +
  labs(title = "Distribution of Household Income",
       x = "Household Income",
       y = "Count") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```
```{r}
ggplot(cleaned_data, aes(x = hhld_inc, fill = hhld_inc)) +
  geom_bar() +
  labs(title = "Distribution of Household Income",
       x = "Household Income",
       y = "Count") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```
```{r}
ggplot(cleaned_data, aes(x = factor(hhld_inc, levels = unique(hhld_inc)), fill = hhld_inc)) +
  geom_bar() +
  labs(title = "Distribution of Household Income",
       x = "Household Income",
       y = "Count") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) 
```
```{r}
ggplot(cleaned_data, aes(x = factor(hhld_inc, levels = unique(cleaned_data$hhld_inc)), fill = hhld_inc)) +
  geom_bar() +
  labs(title = "Distribution of Household Income",
       x = "Household Income",
       y = "Count") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```
# Discussion

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.

## Second discussion point

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {-}

# Additional data details

# Model details {#sec-model-details}

## Posterior predictive check

In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...

In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-ppcheckandposteriorvsprior
#| layout-ncol: 2
#| fig-cap: "Examining how the model fits, and is affected by, the data"
#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]

pp_check(first_model) +
  theme_classic() +
  theme(legend.position = "bottom")

posterior_vs_prior(first_model) +
  theme_minimal() +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom") +
  coord_flip()
```

## Diagnostics

@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...

@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-stanareyouokay
#| fig-cap: "Checking the convergence of the MCMC algorithm"
#| fig-subcap: ["Trace plot", "Rhat plot"]
#| layout-ncol: 2

plot(first_model, "trace")

plot(first_model, "rhat")
```

\newpage

# References

### 2024-02-13 outputs/paper/paper.qmd
Work on data section and update readme

@@
 ---
-title: "My title"
-subtitle: "My subtitle if needed"
+title: ""
 author: 
@@
 number-sections: true
-bibliography: references.bib
 ---
@@
 library(tidyverse)
-
+library(here)
+library(knitr)
 cleaned_data <- read_csv(here::here("outputs/Data/analysis_data.csv"))
@@
 
-You can and should cross-reference sections and sub-sections.
+# Data {#sec-data}
+## Data Introduction {#sec-dataintro}
+The data used in this paper is from (cite og paper).
+The data used in the paper is extremely complicated as it combines numerous data sets to complete their analysis.
+In this paper, we wanted to simplify the data.
+To simply the original papers data we focused on one of their eleven data sets.
+The most comprehensive data set was their baseline data.
+This data was collected through a facebook ad.
+The respondents answered a number of questions including questions about income, ethnicity, family, political beliefs and political following.
+The data was cleaned to focus on respondents income, race and how closely they follow politics.
+This provided a data set that could answer a number of questions.
+To first understand the possible research questions the data it must to be visualized as it has nearly 6000 entries.
 
-The remainder of this paper is structured as follows. @sec-data....
-
-# Data {#sec-data}
-
-The data used in this paper is from (cite og paper).
-The data used in the paper is extremely compplicated as it combines numerous data sets to complete their analysis.
-In this paper, we wanted to simplify the data
+## Income Data {#sec-income_data}
+The first visualization of the data is in @figure1.
+This table illustrates that the least number of households make greater than 100,000 USD, below 20,000USD or preferred not to answer.
+This closely resembles the expected distribution of USA household income.
+As expected in any income distribution the majority of responses fall within the average income ranges of the USA, between 20,000USD and 100,000USD
 ```{r}
-
+#| label: fig-figure1
+#| fig-cap: "Distribution of Income in Responses"
+#| warning: false
+#| message: false
+#| echo: false
 ggplot(cleaned_data, aes(x = reorder(hhld_inc, -table(hhld_inc)[hhld_inc]), fill = hhld_inc)) +
   geom_bar() +
-  labs(title = "Distribution of Household Income",
-       x = "Household Income",
-       y = "Count") +
+  labs(x = "Household Income",
+       y = "Number of Respondents") +
   theme(axis.text.x = element_text(angle = 45, hjust = 1))
@@
 ```
+## Ethnicity Data {#sec-race_data}
+describe table and its implications and relevence
 ```{r}
-ggplot(cleaned_data, aes(x = hhld_inc, fill = hhld_inc)) +
-  geom_bar() +
-  labs(title = "Distribution of Household Income",
-       x = "Household Income",
-       y = "Count") +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1))
+#| label: tbl-race_dist
+#| tbl-cap: "Percentage of each Ethnicity Within the Data"
+#| warning: false
+#| message: false
+#| echo: false
+proportion_table <- cleaned_data %>%
+  group_by(race) %>%
+  summarise((proportion = n() / nrow(cleaned_data))*100) 
+kable(proportion_table)
+
 ```
-```{r}
-ggplot(cleaned_data, aes(x = factor(hhld_inc, levels = unique(hhld_inc)), fill = hhld_inc)) +
-  geom_bar() +
-  labs(title = "Distribution of Household Income",
-       x = "Household Income",
-       y = "Count") +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1)) 
-```
-```{r}
-ggplot(cleaned_data, aes(x = factor(hhld_inc, levels = unique(cleaned_data$hhld_inc)), fill = hhld_inc)) +
-  geom_bar() +
-  labs(title = "Distribution of Household Income",
-       x = "Household Income",
-       y = "Count") +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1))
-```
+
+## Politics Data {#sec-pol_data}
+
+# Model
+
+simple regression of income and politics data controlling for race
+
 # Discussion
@@
 
-## Posterior predictive check
-
-In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...
-
-In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...
-
-```{r}
-#| eval: true
-#| echo: false
-#| message: false
-#| warning: false
-#| label: fig-ppcheckandposteriorvsprior
-#| layout-ncol: 2
-#| fig-cap: "Examining how the model fits, and is affected by, the data"
-#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]
-
-pp_check(first_model) +
-  theme_classic() +
-  theme(legend.position = "bottom")
-
-posterior_vs_prior(first_model) +
-  theme_minimal() +
-  scale_color_brewer(palette = "Set1") +
-  theme(legend.position = "bottom") +
-  coord_flip()
-```
-
-## Diagnostics
-
-@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...
-
-@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...
-
-```{r}
-#| echo: false
-#| eval: true
-#| message: false
-#| warning: false
-#| label: fig-stanareyouokay
-#| fig-cap: "Checking the convergence of the MCMC algorithm"
-#| fig-subcap: ["Trace plot", "Rhat plot"]
-#| layout-ncol: 2
-
-plot(first_model, "trace")
-
-plot(first_model, "rhat")
-```
-
 \newpage

### 2024-02-14 outputs/paper/paper.qmd
Updates to scripts - almost finished data section

@@
 author: 
-  - First author
-  - Another author
-thanks: "Code and data are available at: LINK."
+  - Gavin Crooks
+  - Samarth Rajani
+thanks: "Code and data are available at: LINK.https://github.com/Crooksyyy/The-Effects-of-Social-Media"
 date: today
@@
 number-sections: true
+toc: true
+bibliography: references.bib 
+nocite: |
+  @*
 ---
@@
 The data used in the paper is extremely complicated as it combines numerous data sets to complete their analysis.
-In this paper, we wanted to simplify the data.
-To simply the original papers data we focused on one of their eleven data sets.
-The most comprehensive data set was their baseline data.
+In this paper, we wanted to simplify the data to determine if their paper had underlying biases within the data.
+To do this we focused on one of their eleven data sets, baseline dataset as it was the most comprehensive.
 This data was collected through a facebook ad.
 The respondents answered a number of questions including questions about income, ethnicity, family, political beliefs and political following.
-The data was cleaned to focus on respondents income, race and how closely they follow politics.
-This provided a data set that could answer a number of questions.
-To first understand the possible research questions the data it must to be visualized as it has nearly 6000 entries.
+THis is a very useful data set outside the scope of the original paper as it can be analyzed to answer a number of questions.
+The data set was cleaned to focus on respondents income, race and how closely they follow politics.
+This provided a data set of approximately 6000 complete responses after removing unfinished responses.
+This was a substantial decrease from the orignal 24000 responses in the data.
 
 ## Income Data {#sec-income_data}
-The first visualization of the data is in @figure1.
-This table illustrates that the least number of households make greater than 100,000 USD, below 20,000USD or preferred not to answer.
-This closely resembles the expected distribution of USA household income.
-As expected in any income distribution the majority of responses fall within the average income ranges of the USA, between 20,000USD and 100,000USD
+The variable within the data was the income variable.
+The questionnaire included a categorical value for the the household income of respondents.
+The data can be visualized in @figure1.
+This graph illustrates that the least number of households make greater than 100,000 USD, below 20,000USD or preferred not to answer.
+This graph also shows what the categorical option were for the respondents to the questionnaire.
+@figure1 closely resembles the expected distribution of USA household income.
+As expected in any income distribution the majority of responses fall within the average income ranges of the USA, between 20,000USD and 100,000USD.
+These factors indicate that the data set has an accurate respresentation of household income.
 ```{r}
 #| label: fig-figure1
-#| fig-cap: "Distribution of Income in Responses"
+#| fig-cap: "Distribution of Income from Responses in a facebook ad"
 #| warning: false
@@
 ## Ethnicity Data {#sec-race_data}
-describe table and its implications and relevence
+The second question of the data that we have included in our analysis is the ethnicity of the respondents.
+This again is a categorical variable, that the individual self identifies their own ethnicity.
+The response options included Asian or Pacific Islander, White / Caucasian, Hispanic, Black or African American and other.
+@race_dist shows the percentage of respondents in each  with the overwhelming majority of responses being Caucasian at nearly 70%.
+This is actually less than the most recent estimates by the United States government which estimate over 75% of the population is Caucasian (cite us gov).
+The data also has an over representation of Asian and Native Americans.
+This results in an under representation of Hispanic and African American populations.
+
+https://www.census.gov/quickfacts/fact/table/US/PST045222
+
 ```{r} 
 #| label: tbl-race_dist
-#| tbl-cap: "Percentage of each Ethnicity Within the Data"
+#| tbl-cap: "Percentage of each Ethnicity from Responses in a facebook ad"
 #| warning: false
@@
   summarise((proportion = n() / nrow(cleaned_data))*100) 
-kable(proportion_table)
-
+kable(proportion_table,
+      col.names = c("Ethnicity", "Percentage of Responses")
+)
 ```
@@
 
+The third variable in the data that is included in our analysis is a variable of respondents self identifying how closely they follow politics.
+This is another categorical variable measured as Not at all closely, Somewhat closely, Rather closely and  Very closely.
+This variable faces many problems as this categorical scale is not consistent across respondents.
+To be specific we mean someone who identifies as someone who does follows Not at all closely can be following politics more than someone who identifies as Somewhat closely.
+This is a measurement issue within to the questions asked in the survey and all self identifying variables in general.
+```{r}
+#| label: fig-figure2
+#| fig-cap: "How Closely People Follow Politics from Responses in a facebook ad"
+#| warning: false
+#| message: false
+#| echo: false
+
+ggplot(cleaned_data, aes(x = "", fill = follow_politics)) +
+  geom_bar() +
+  coord_polar("y") +
+  labs(fill = "Legend") +
+  theme(axis.title = element_blank())
+
+```
 # Model

### 2024-02-14 outputs/paper/paper.tex
Updates to scripts - almost finished data section

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  letterpaper,
  DIV=11,
  numbers=noendperiod]{scrartcl}

\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else  
    % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{5}
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
% definitions for citeproc citations
\NewDocumentCommand\citeproctext{}{}
\NewDocumentCommand\citeproc{mm}{%
  \begingroup\def\citeproctext{#2}\cite{#1}\endgroup}
\makeatletter
 % allow citations to break across lines
 \let\@cite@ofmt\@firstofone
 % avoid brackets around text for \cite:
 \def\@biblabel#1{}
 \def\@cite#1#2{{#1\if@tempswa , #2\fi}}
\makeatother
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-indent, #2 entry-spacing
 {\begin{list}{}{%
  \setlength{\itemindent}{0pt}
  \setlength{\leftmargin}{0pt}
  \setlength{\parsep}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
   \setlength{\leftmargin}{\cslhangindent}
   \setlength{\itemindent}{-1\cslhangindent}
  \fi
  % set entry spacing
  \setlength{\itemsep}{#2\baselineskip}}}
 {\end{list}}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{\hfill\break\parbox[t]{\linewidth}{\strut\ignorespaces#1\strut}}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\KOMAoption{captions}{tableheading}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage{bookmark}

\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdfauthor={Gavin Crooks; Samarth Rajani},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\author{Gavin Crooks \and Samarth Rajani}
\date{February 14, 2024}

\begin{document}

\renewcommand*\contentsname{Table of contents}
{
\hypersetup{linkcolor=}
\setcounter{tocdepth}{3}
\tableofcontents
}
\section{Introduction}\label{introduction}

The introduction is self-contained and tells a reader everything they
need to know including: 1) broader context to motivate; 2) some detail
about what the paper is about; 3) a clear gap that needs to be filled;
4) what was done; 5) what was found; 6) why it is important; 7) the
structure of the paper. A reader should be able to read only the
introduction and know what was done, why, and what was found. Likely 3
or 4 paragraphs, or 10 per cent of total.

\section{Data}\label{sec-data}

\subsection{Data Introduction}\label{sec-dataintro}

The data used in this paper is from (cite og paper). The data used in
the paper is extremely complicated as it combines numerous data sets to
complete their analysis. In this paper, we wanted to simplify the data
to determine if their paper had underlying biases within the data. To do
this we focused on one of their eleven data sets, baseline dataset as it
was the most comprehensive. This data was collected through a facebook
ad. The respondents answered a number of questions including questions
about income, ethnicity, family, political beliefs and political
following. THis is a very useful data set outside the scope of the
original paper as it can be analyzed to answer a number of questions.
The data set was cleaned to focus on respondents income, race and how
closely they follow politics. This provided a data set of approximately
6000 complete responses after removing unfinished responses. This was a
substantial decrease from the orignal 24000 responses in the data.

\subsection{Income Data}\label{sec-income_data}

The variable within the data was the income variable. The questionnaire
included a categorical value for the the household income of
respondents. The data can be visualized in (\textbf{figure1?}). This
graph illustrates that the least number of households make greater than
100,000 USD, below 20,000USD or preferred not to answer. This graph also
shows what the categorical option were for the respondents to the
questionnaire. (\textbf{figure1?}) closely resembles the expected
distribution of USA household income. As expected in any income
distribution the majority of responses fall within the average income
ranges of the USA, between 20,000USD and 100,000USD. These factors
indicate that the data set has an accurate respresentation of household
income.

\begin{figure}

\centering{

\includegraphics{paper_files/figure-pdf/fig-figure1-1.pdf}

}

\caption{\label{fig-figure1}Distribution of Income from Responses in a
facebook ad}

\end{figure}%

\subsection{Ethnicity Data}\label{sec-race_data}

The second question of the data that we have included in our analysis is
the ethnicity of the respondents. This again is a categorical variable,
that the individual self identifies their own ethnicity. The response
options included Asian or Pacific Islander, White / Caucasian, Hispanic,
Black or African American and other. (\textbf{race\_dist?}) shows the
percentage of respondents in each with the overwhelming majority of
responses being Caucasian at nearly 70\%. This is actually less than the
most recent estimates by the United States government which estimate
over 75\% of the population is Caucasian (cite us gov). The data also
has an over representation of Asian and Native Americans. This results
in an under representation of Hispanic and African American populations.

https://www.census.gov/quickfacts/fact/table/US/PST045222

\begin{longtable}[]{@{}lr@{}}

\caption{\label{tbl-race\_dist}Percentage of each Ethnicity from
Responses in a facebook ad}

\tabularnewline

\toprule\noalign{}
Ethnicity & Percentage of Responses \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
American Indian or Alaskan Native & 0.7554138 \\
Asian or Pacific Islander & 13.5806614 \\
Black or African American & 6.0936713 \\
Hispanic & 8.0577472 \\
Other (please specify) & 2.5851939 \\
White / Caucasian & 68.9273124 \\

\end{longtable}

\subsection{Politics Data}\label{sec-pol_data}

The third variable in the data that is included in our analysis is a
variable of respondents self identifying how closely they follow
politics. This is another categorical variable measured as Not at all
closely, Somewhat closely, Rather closely and Very closely. This
variable faces many problems as this categorical scale is not consistent
across respondents. To be specific we mean someone who identifies as
someone who does follows Not at all closely can be following politics
more than someone who identifies as Somewhat closely. This is a
measurement issue within to the questions asked in the survey and all
self identifying variables in general.

\begin{figure}

\centering{

\includegraphics{paper_files/figure-pdf/fig-figure2-1.pdf}

}

\caption{\label{fig-figure2}How Closely People Follow Politics from
Responses in a facebook ad}

\end{figure}%

\section{Model}\label{model}

simple regression of income and politics data controlling for race

\section{Discussion}\label{discussion}

\subsection{First discussion point}\label{sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The
discussion is a chance to show off what you know and what you learnt
from all this.

\subsection{Second discussion point}\label{second-discussion-point}

\subsection{Third discussion point}\label{third-discussion-point}

\subsection{Weaknesses and next steps}\label{weaknesses-and-next-steps}

Weaknesses and next steps should also be included.

\newpage

\appendix

\section*{Appendix}\label{appendix}
\addcontentsline{toc}{section}{Appendix}

\section{Additional data details}\label{additional-data-details}

\section{Model details}\label{sec-model-details}

\newpage

\section*{References}\label{references}
\addcontentsline{toc}{section}{References}

\phantomsection\label{refs}
\begin{CSLReferences}{1}{0}
\bibitem[\citeproctext]{ref-citeLahman}
Friendly, Michael, Chris Dalzell, Martin Monkman, and Dennis Murphy.
2020. \emph{Lahman: Sean {``Lahman''} Baseball Database}.
\url{https://CRAN.R-project.org/package=Lahman}.

\bibitem[\citeproctext]{ref-gebru2021datasheets}
Gebru, Timnit, Jamie Morgenstern, Briana Vecchione, Jennifer Wortman
Vaughan, Hanna Wallach, Hal Daumé Iii, and Kate Crawford. 2021.
{``Datasheets for Datasets.''} \emph{Communications of the ACM} 64 (12):
86--92.

\bibitem[\citeproctext]{ref-rstanarm}
Goodrich, Ben, Jonah Gabry, Imad Ali, and Sam Brilleman. 2022.
{``Rstanarm: {Bayesian} Applied Regression Modeling via {Stan}.''}
\url{https://mc-stan.org/rstanarm/}.

\bibitem[\citeproctext]{ref-palmerpenguins}
Horst, Allison Marie, Alison Presmanes Hill, and Kristen B Gorman. 2020.
\emph{Palmerpenguins: Palmer Archipelago (Antarctica) Penguin Data}.
\url{https://doi.org/10.5281/zenodo.3960218}.

\bibitem[\citeproctext]{ref-citeR}
R Core Team. 2022. \emph{R: A Language and Environment for Statistical
Computing}. Vienna, Austria: R Foundation for Statistical Computing.
\url{https://www.R-project.org/}.

\bibitem[\citeproctext]{ref-thereferencecanbewhatever}
Wickham, Hadley, Mara Averick, Jennifer Bryan, Winston Chang, Lucy
D'Agostino McGowan, Romain François, Garrett Grolemund, et al. 2019.
{``Welcome to the {tidyverse}.''} \emph{Journal of Open Source Software}
4 (43): 1686. \url{https://doi.org/10.21105/joss.01686}.

\end{CSLReferences}

\end{document}

### 2024-02-14 scripts/01-download_data.R

@@ -11,17 +11,15 @@
 #### Workspace setup ####
 library(haven)
 library(tidyverse)
+library(data.table)
 
 #### Download data ####
-sms_data <- read_dta("~/Desktop/112081-V1 2/sms_anonymous.dta")
-data1 <- read_dta("raw/anes_timeseries_2016.dta")
-politics_data <- read_dta("~/Desktop/112081-V1 2/politics_anonymous.dta")
-base_data <- read_dta("~/Desktop/112081-V1 2/baseline_anonymous.dta")
+### Data can be downloaded from the URL below as file format does not allow it to be opened directly or from folder in repo 
+# https://www.openicpsr.org/openicpsr/project/112081/version/V1/view?path=/openicpsr/112081/fcr:versions/V1/confidential/main_experiment/output/baseline_anonymous.dta&type=file
+
+base_data <- read_dta("inputs/data/base_data.dta")
 
 
 #### Save data ####
-write_csv(data1, "inputs/data/raw_election_data.csv") 
-write_csv(sms_data, "inputs/data/sms_data.csv")
-write_csv(politics_data, "inputs/data/politics_data.csv")
 write_csv(base_data,"inputs/data/base_data.csv" )
 

### 2024-02-14 scripts/02-data_cleaning.R

@@ -11,14 +11,9 @@ library(tidyverse)
 
 #### Clean data ####
 raw_data <- read_csv("inputs/data/base_data.csv")
-View(raw_data)
 cleaned_data <- select(raw_data, hhld_inc, race, follow_politics)
-cleaned_data
-
-cleaned_data <- cleaned_data |> 
+cleaned_data <- cleaned_data %>% 
   drop_na()
-
-
 view(cleaned_data)
 #### Save data ####
 write_csv(cleaned_data, "outputs/data/analysis_data.csv")

### 2024-02-14 outputs/paper/paper.qmd
work

@@
 ---
-title: ""
+title: "Paper 2"
 author: 
@@
 As expected in any income distribution the majority of responses fall within the average income ranges of the USA, between 20,000USD and 100,000USD.
-These factors indicate that the data set has an accurate respresentation of household income.
+These factors indicate that the data set has an accurate representation of household income.
 ```{r}
@@
 #| echo: false
+
 ggplot(cleaned_data, aes(x = reorder(hhld_inc, -table(hhld_inc)[hhld_inc]), fill = hhld_inc)) +
@@
        y = "Number of Respondents") +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1))
+  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
+  guides(fill = FALSE) # Code from Stack overflow
 
@@
 This is a measurement issue within to the questions asked in the survey and all self identifying variables in general.
+@figure2 shows the quantity of respondents in each group.
+The most common response is that they follow somewhat closely and the other responses are relatively even.
 ```{r}
@@
 ```
+## Missing Data {#sec-Missing_data}
+
 # Model
@@
 # Discussion
-
+like to incluse variables like state etc data set too small/ incomplete for that
 ## First discussion point {#sec-first-point}

### 2024-02-14 outputs/paper/paper.tex
work

@@
 \hypersetup{
+  pdftitle={Paper 2},
   pdfauthor={Gavin Crooks; Samarth Rajani},
@@
 
+\title{Paper 2\thanks{Code and data are available at:
+LINK.https://github.com/Crooksyyy/The-Effects-of-Social-Media}}
 \author{Gavin Crooks \and Samarth Rajani}
@@
 \begin{document}
+\maketitle
+\begin{abstract}
+First sentence. Second sentence. Third sentence. Fourth sentence.
+\end{abstract}
 
@@
 ranges of the USA, between 20,000USD and 100,000USD. These factors
-indicate that the data set has an accurate respresentation of household
+indicate that the data set has an accurate representation of household
 income.
@@
 measurement issue within to the questions asked in the survey and all
-self identifying variables in general.
+self identifying variables in general. (\textbf{figure2?}) shows the
+quantity of respondents in each group. The most common response is that
+they follow somewhat closely and the other responses are relatively
+even.
 
@@
 
+\subsection{Missing Data}\label{sec-Missing_data}
+
 \section{Model}\label{model}
@@
 
-\subsection{First discussion point}\label{sec-first-point}
+like to incluse variables like state etc data set too small/ incomplete
+for that \#\# First discussion point \{\#sec-first-point\}
 

### 2024-02-14 scripts/01-download_data.R

@@ -19,7 +19,6 @@ library(data.table)
 
 base_data <- read_dta("inputs/data/base_data.dta")
 
-
 #### Save data ####
 write_csv(base_data,"inputs/data/base_data.csv" )
 

### 2024-02-15 scripts/00-simulate_data.R
update to scripts

@@ -1,19 +1,59 @@
 #### Preamble ####
-# Purpose: Simulates... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
-# License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
-
+# Purpose: Simulates data set used in analysis to be able to test data
+# Author: Gavin Crooks and Samarth Rajani
+# Date: 14 February 2024 
+# Contact: gavin.crooks@mail.utoronto.ca or samarth.rajani@mail.utoronto.ca
+# Pre-requisites: N/A
 
 #### Workspace setup ####
 library(tidyverse)
-# [...UPDATE THIS...]
+
 
 #### Simulate data ####
-# [...ADD CODE HERE...]
+# Set seed for reproducibility
+set.seed(93)
+
+# Number of samples
+num_samples <- 5000
+
+# Household Income 
+income_categories <- c("$60,000 to $74,999", "$50,000 to $59,999",  "$40,000 to $49,999",
+                       "$100,000 to $124,999", "Prefer not to answer", "$10,000 to $19,999",
+                       "$75,000 to $99,999", "0 to $9,999", "$20,000 to $29,999",
+                       "$30,000 to $39,999", "$125,000 to $149,999", "$150,000 and up")
+household_income <- sample(income_categories, size = num_samples, replace = TRUE)
+
+# Ethnicity categories
+race_categories <- c("Asian or Pacific Islander", "White / Caucasian", "Hispanic",
+                     "Black or African American", "other")
+race <- sample(race_categories, size = num_samples, replace = TRUE,
+               prob = c(0.075,0.75,0.125,0.9,0.1))
+
+# Follows Politics 
+follow_politics_categories <- c("Somewhat closely", "Not at all closely", 
+                         "Very closely", "Rather closely")
+follows_politics <- sample(follow_politics_categories, size = num_samples, replace = TRUE,
+                           prob = c(0.2,0.2,0.25,0.35))
+
+# Follows Trump 
+follows_trump_categories <- c("Somewhat closely", "Not at all closely", 
+                              "Very closely", "Rather closely")
+follows_trump <- sample(follows_trump_categories, size = num_samples, replace = TRUE)
+
[…]

### 2024-02-15 scripts/01-download_data.R

@@ -1,9 +1,8 @@
 #### Preamble ####
-# Purpose: Saves the Data into Repo as CSV 
+# Purpose: Saves the Data into Repo as CSV and as original dta file
 # Author: Gavin Crooks and Samarth Rajani
 # Date: Feb 12, 2024
 # Contact: gavin.crooks@mail.utoronto.ca or samarth.rajani@mail.utoronto.ca
-# License: MIT
 # Pre-requisites: N/A
 
 

### 2024-02-15 scripts/00-simulate_data.R
Finished Scripts

@@ -25,9 +25,9 @@ household_income <- sample(income_categories, size = num_samples, replace = TRUE
 
 # Ethnicity categories
 race_categories <- c("Asian or Pacific Islander", "White / Caucasian", "Hispanic",
-                     "Black or African American", "other")
+                     "Black or African American", "American Indian or Alaskan Native", "other")
 race <- sample(race_categories, size = num_samples, replace = TRUE,
-               prob = c(0.075,0.75,0.125,0.9,0.1))
+               prob = c(0.075,0.75,0.125,0.9,0.075,0.05))
 
 # Follows Politics 
 follow_politics_categories <- c("Somewhat closely", "Not at all closely", 
@@ -52,7 +52,7 @@ sim_data <- data.frame(
 head(data)
 
 # Save simulated data
-write_csv(sim_data,"inputs/data/simulated_data.csv" )
+write_csv(sim_data,"outputs/data/simulated_data.csv" )
 
 
 

### 2024-02-15 scripts/02-data_cleaning.R

@@ -11,9 +11,10 @@ library(tidyverse)
 
 #### Clean data ####
 raw_data <- read_csv("inputs/data/base_data.csv")
-cleaned_data <- select(raw_data, hhld_inc, race, follow_politics)
+cleaned_data <- select(raw_data, hhld_inc, race, follow_politics, follow_trump)
 cleaned_data <- cleaned_data %>% 
   drop_na()
 view(cleaned_data)
+
 #### Save data ####
 write_csv(cleaned_data, "outputs/data/analysis_data.csv")

### 2024-02-15 scripts/03-test_data.R

@@ -1,15 +1,44 @@
 #### Preamble ####
-# Purpose: Tests... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
-# License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Purpose: Tests our simulated data, then test the actual data set to ensure data cleaning is done and the data set is as expected
+# Author: Gavin Crooks and Samarth Rajani
+# Date: 14 February 2024 
+# Contact: gavin.crooks@mail.utoronto.ca or samarth.rajani@mail.utoronto.ca
+# Pre-requisites: 01-download_data and 02-data_cleaning or 00-simulate_data 
 
 
 #### Workspace setup ####
 library(tidyverse)
-# [...UPDATE THIS...]
 
 #### Test data ####
+# Open data
+cleaned_data <- read_csv("outputs/Data/analysis_data.csv")
+
+# Test correct number of catergies for each variable
+cleaned_data$follow_trump|>
+  unique() %>% 
+  length() == 4
+
+cleaned_data$follow_politics|>
+  unique() %>% 
+  length() == 4
+
+cleaned_data$race|>
+  unique() %>% 
+  length() == 6
+
+cleaned_data$hhld_inc|>
+  unique() %>% 
+  length() == 12
+
+
+#Test value types 
+#is.character code from stack overflow
+is.character(cleaned_data$hhld_inc)
+is.character(cleaned_data$follow_trump)
+is.character(cleaned_data$follow_politics)
+is.character(cleaned_data$race)
+
+# or 
+
+sapply(cleaned_data, class)
+

### 2024-02-15 outputs/paper/paper.qmd
added new graph

@@
 
+```{r}
+# Parts of this code from R-charts
+#https://r-charts.com/part-whole/stacked-bar-chart-ggplot2/
+ggplot(cleaned_data, aes(x = follow_trump, fill = race)) +
+  geom_bar(position = 'stack', color = 'black', stat = 'count') +
+  labs(title = "Number of People Following Trump by Race",
+       x = "Follows Trump",
+       y = "Count") +
+  scale_fill_manual(values = c('White / Caucasian' = 'lightblue', 'Black or African American' = 'lightcoral', 'Asian or Pacific Islander' = 'lightgreen', 'Hispanic' = 'plum',
+                               'Other  (please specify)' = 'lightgoldenrodyellow')) +
+  theme_minimal()
+
+```
 # Model

### 2024-02-15 outputs/paper/paper.tex
added new graph

@@
 \fi
+
+\usepackage{color}
+\usepackage{fancyvrb}
+\newcommand{\VerbBar}{|}
+\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
+\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
+% Add ',fontsize=\small' for more characters per line
+\usepackage{framed}
+\definecolor{shadecolor}{RGB}{241,243,245}
+\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
+\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
+\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
+\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.40,0.45,0.13}{#1}}
+\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
+\newcommand{\BuiltInTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
+\newcommand{\CharTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
+\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
+\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{\textit{#1}}}
+\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
+\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
+\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
+\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
+\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{\textit{#1}}}
+\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
+\newcommand{\ExtensionTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
+\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
+\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.28,0.35,0.67}{#1}}
+\newcommand{\ImportTok}[1]{\textcolor[rgb]{0.00,0.46,0.62}{#1}}
+\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
+\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
+\newcommand{\NormalTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
+\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
+\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
+\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
+\newcommand{\RegionMarkerTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
+\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
+\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
+\newcommand{\StringTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
+\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.07,0.07,0.07}{#1}}
+\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
+\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{\textit{#1}}}
 
@@
 
+\begin{Shaded}
+\begin{Highlighting}[]
+\CommentTok{\# Parts of this code from R{-}charts}
+\CommentTok{\#https://r{-}charts.com/part{-}whole/stacked{-}bar{-}chart{-}ggplot2/}
+\FunctionTok{ggplot}\NormalTok{(cleaned\_data, }\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ follow\_trump, }\AttributeTok{fill =}\NormalTok{ race)) }\SpecialCharTok{+}
+  \FunctionTok{geom\_bar}\NormalTok{(}\AttributeTok{position =} \StringTok{\textquotesingle{}stack\textquotesingle{}}\NormalTok{, }\AttributeTok{color =} \StringTok{\textquotesingle{}black\textquotesingle{}}\NormalTok{, }\AttributeTok{stat =} \StringTok{\textquotesingle{}count\textquotesingle{}}\NormalTok{) }\SpecialCharTok{+}
+  \FunctionTok{labs}\NormalTok{(}\AttributeTok{title =} \StringTok{"Number of People Following Trump by Race"}\NormalTok{,}
+       \AttributeTok{x =} \StringTok{"Follows Trump"}\NormalTok{,}
+       \AttributeTok{y =} \StringTok{"Count"}\NormalTok{) }\SpecialCharTok{+}
+  \FunctionTok{scale\_fill\_manual}\NormalTok{(}\AttributeTok{values =} \FunctionTok{c}\NormalTok{(}\StringTok{\textquotesingle{}White / Caucasian\textquotesingle{}} \OtherTok{=} \StringTok{\textquotesingle{}lightblue\textquotesingle{}}\NormalTok{, }\StringTok{\textquotesingle{}Black or African American\textquotesingle{}} \OtherTok{=} \StringTok{\textquotesingle{}lightcoral\textquotesingle{}}\NormalTok{, }\StringTok{\textquotesingle{}Asian or Pacific Islander\textquotesingle{}} \OtherTok{=} \StringTok{\textquotesingle{}lightgreen\textquotesingle{}}\NormalTok{, }\StringTok{\textquotesingle{}Hispanic\textquotesingle{}} \OtherTok{=} \StringTok{\textquotesingle{}plum\textquotesingle{}}\NormalTok{,}
+                               \StringTok{\textquotesingle{}Other  (please specify)\textquotesingle{}} \OtherTok{=} \StringTok{\textquotesingle{}lightgoldenrodyellow\textquotesingle{}}\NormalTok{)) }\SpecialCharTok{+}
+  \FunctionTok{theme\_minimal}\NormalTok{()}
+\end{Highlighting}
+\end{Shaded}
+
+\includegraphics{paper_files/figure-pdf/unnamed-chunk-5-1.pdf}
+
 \section{Model}\label{model}

### 2024-02-15 scripts/02-data_cleaning.R

@@ -14,7 +14,10 @@ raw_data <- read_csv("inputs/data/base_data.csv")
 cleaned_data <- select(raw_data, hhld_inc, race, follow_politics, follow_trump)
 cleaned_data <- cleaned_data %>% 
   drop_na()
+
+
 view(cleaned_data)
 
 #### Save data ####
 write_csv(cleaned_data, "outputs/data/analysis_data.csv")
+

### 2024-02-15 scripts/03-test_data.R

@@ -11,7 +11,7 @@ library(tidyverse)
 
 #### Test data ####
 # Open data
-cleaned_data <- read_csv("outputs/Data/analysis_data.csv")
+cleaned_data <- read_csv("outputs/data/analysis_data.csv")
 
 # Test correct number of catergies for each variable
 cleaned_data$follow_trump|>

### 2024-02-15 outputs/paper/paper.qmd
new graph

@@
   theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
-  guides(fill = FALSE) # Code from Stack overflow
+  guides(fill = FALSE) # Parts of the code from Stack overflow
 
@@
 ```
+```{r}
+#Decrease from 12 income groups to 4 
+# help from stack overflow 
+#https://stackoverflow.com/questions/28190435/changing-factor-levels-with-dplyr-mutate
+cleaned_data <- cleaned_data %>%
+  mutate(income_group = case_when(
+    hhld_inc %in% c("$0 to $9,999", "$10,000 to $19,999") ~ "$0 to $19,999",
+    hhld_inc %in% c("$20,000 to $29,999", "$30,000 to $39,999", "$40,000 to $49,999") ~ "$20,000 to $49,999",
+    hhld_inc %in% c("$50,000 to $59,999", "$60,000 to $74,999", "$75,000 to $99,999") ~ "$50,000 to $99,999",
+    hhld_inc %in% c("$100,000 to $124,999", "$125,000 to $149,999", "$150,000 and up") ~ "$100,000 and up",
+    TRUE ~ "Prefer not to answer"
+  ))
+
+ggplot(cleaned_data, aes(x = follow_trump, fill = income_group)) +
+  geom_bar(position = 'stack', color = 'black', stat = 'count') +
+  labs(title = "Number of People Following Trump by Income Group",
+       x = "Follows Trump",
+       y = "Count") +
+  scale_fill_manual(values = c(
+    "$0 to $19,999" = 'lightblue',
+    "$20,000 to $49,999" = 'lightcoral',
+    "$50,000 to $99,999" = 'lightgreen',
+    "$100,000 and up" = 'plum',
+    "Unknown or Prefer not to answer" = 'lightgrey'
+  )) +
+  theme_minimal()
+
+```
 # Model

### 2024-02-15 outputs/paper/paper.tex
new graph

@@
 
+\begin{Shaded}
+\begin{Highlighting}[]
+\CommentTok{\#Decrease from 12 income groups to 4 }
+\CommentTok{\# help from stack overflow }
+\CommentTok{\#https://stackoverflow.com/questions/28190435/changing{-}factor{-}levels{-}with{-}dplyr{-}mutate}
+\NormalTok{cleaned\_data }\OtherTok{\textless{}{-}}\NormalTok{ cleaned\_data }\SpecialCharTok{\%\textgreater{}\%}
+  \FunctionTok{mutate}\NormalTok{(}\AttributeTok{income\_group =} \FunctionTok{case\_when}\NormalTok{(}
+\NormalTok{    hhld\_inc }\SpecialCharTok{\%in\%} \FunctionTok{c}\NormalTok{(}\StringTok{"$0 to $9,999"}\NormalTok{, }\StringTok{"$10,000 to $19,999"}\NormalTok{) }\SpecialCharTok{\textasciitilde{}} \StringTok{"$0 to $19,999"}\NormalTok{,}
+\NormalTok{    hhld\_inc }\SpecialCharTok{\%in\%} \FunctionTok{c}\NormalTok{(}\StringTok{"$20,000 to $29,999"}\NormalTok{, }\StringTok{"$30,000 to $39,999"}\NormalTok{, }\StringTok{"$40,000 to $49,999"}\NormalTok{) }\SpecialCharTok{\textasciitilde{}} \StringTok{"$20,000 to $49,999"}\NormalTok{,}
+\NormalTok{    hhld\_inc }\SpecialCharTok{\%in\%} \FunctionTok{c}\NormalTok{(}\StringTok{"$50,000 to $59,999"}\NormalTok{, }\StringTok{"$60,000 to $74,999"}\NormalTok{, }\StringTok{"$75,000 to $99,999"}\NormalTok{) }\SpecialCharTok{\textasciitilde{}} \StringTok{"$50,000 to $99,999"}\NormalTok{,}
+\NormalTok{    hhld\_inc }\SpecialCharTok{\%in\%} \FunctionTok{c}\NormalTok{(}\StringTok{"$100,000 to $124,999"}\NormalTok{, }\StringTok{"$125,000 to $149,999"}\NormalTok{, }\StringTok{"$150,000 and up"}\NormalTok{) }\SpecialCharTok{\textasciitilde{}} \StringTok{"$100,000 and up"}\NormalTok{,}
+    \ConstantTok{TRUE} \SpecialCharTok{\textasciitilde{}} \StringTok{"Prefer not to answer"}
+\NormalTok{  ))}
+
+\FunctionTok{ggplot}\NormalTok{(cleaned\_data, }\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ follow\_trump, }\AttributeTok{fill =}\NormalTok{ income\_group)) }\SpecialCharTok{+}
+  \FunctionTok{geom\_bar}\NormalTok{(}\AttributeTok{position =} \StringTok{\textquotesingle{}stack\textquotesingle{}}\NormalTok{, }\AttributeTok{color =} \StringTok{\textquotesingle{}black\textquotesingle{}}\NormalTok{, }\AttributeTok{stat =} \StringTok{\textquotesingle{}count\textquotesingle{}}\NormalTok{) }\SpecialCharTok{+}
+  \FunctionTok{labs}\NormalTok{(}\AttributeTok{title =} \StringTok{"Number of People Following Trump by Income Group"}\NormalTok{,}
+       \AttributeTok{x =} \StringTok{"Follows Trump"}\NormalTok{,}
+       \AttributeTok{y =} \StringTok{"Count"}\NormalTok{) }\SpecialCharTok{+}
+  \FunctionTok{scale\_fill\_manual}\NormalTok{(}\AttributeTok{values =} \FunctionTok{c}\NormalTok{(}
+    \StringTok{"$0 to $19,999"} \OtherTok{=} \StringTok{\textquotesingle{}lightblue\textquotesingle{}}\NormalTok{,}
+    \StringTok{"$20,000 to $49,999"} \OtherTok{=} \StringTok{\textquotesingle{}lightcoral\textquotesingle{}}\NormalTok{,}
+    \StringTok{"$50,000 to $99,999"} \OtherTok{=} \StringTok{\textquotesingle{}lightgreen\textquotesingle{}}\NormalTok{,}
+    \StringTok{"$100,000 and up"} \OtherTok{=} \StringTok{\textquotesingle{}plum\textquotesingle{}}\NormalTok{,}
+    \StringTok{"Unknown or Prefer not to answer"} \OtherTok{=} \StringTok{\textquotesingle{}lightgrey\textquotesingle{}}
+\NormalTok{  )) }\SpecialCharTok{+}
+  \FunctionTok{theme\_minimal}\NormalTok{()}
+\end{Highlighting}
+\end{Shaded}
+
+\includegraphics{paper_files/figure-pdf/unnamed-chunk-6-1.pdf}
+
 \section{Model}\label{model}

### 2024-02-15 outputs/paper/paper.qmd
update again

--- 2024-02-14 outputs/paper/paper.qmd
@@
 
+```{r}
+# Parts of this code from R-charts
+#https://r-charts.com/part-whole/stacked-bar-chart-ggplot2/
+# Assisited by Chat GPT3.5 - view full chat in inputs/llms/usage.txt
+ggplot(cleaned_data, aes(x = follow_trump, fill = race)) +
+  geom_bar(position = 'stack', color = 'black', stat = 'count') +
+  labs(title = "Number of People Following Trump by Race",
+       x = "Follows Trump",
+       y = "Count") +
+  scale_fill_manual(values = c('White / Caucasian' = 'lightblue', 'Black or African American' = 'lightcoral', 'Asian or Pacific Islander' = 'lightgreen', 'Hispanic' = 'plum',
+                               'Other  (please specify)' = 'lightgoldenrodyellow')) +
+  theme_minimal()
+
+```
+```{r}
+#| label: fig-figure3
+#| fig-cap: ""
+#| warning: false
+#| message: false
+#| echo: false
+
+## Assisited by Chat GPT3.5 - view full chat in inputs/llms/usage.txt
+#Decrease from 12 income groups to 4 
+cleaned_data <- cleaned_data %>%
+  mutate(income_group = case_when(
+    hhld_inc %in% c("$0 to $9,999", "$10,000 to $19,999") ~ "$0 to $19,999",
+    hhld_inc %in% c("$20,000 to $29,999", "$30,000 to $39,999", "$40,000 to $49,999") ~ "$20,000 to $49,999",
+    hhld_inc %in% c("$50,000 to $59,999", "$60,000 to $74,999", "$75,000 to $99,999") ~ "$50,000 to $99,999",
+    hhld_inc %in% c("$100,000 to $124,999", "$125,000 to $149,999", "$150,000 and up") ~ "$100,000 and up",
+    TRUE ~ "Prefer not to answer"
+  ))
+
+ggplot(cleaned_data, aes(x = follow_trump, fill = income_group)) +
+  geom_bar(position = 'stack', color = 'black', stat = 'count') +
+  labs(title = "Number of People Following Trump by Income Group",
+       x = "Follows Trump",
+       y = "Count") +
+  scale_fill_manual(values = c(
+    "$0 to $19,999" = 'lightblue',
+    "$20,000 to $49,999" = 'lightcoral',
+    "$50,000 to $99,999" = 'lightgreen',
+    "$100,000 and up" = 'plum',
+    "Unknown or Prefer not to answer" = 'lightgrey'
+  )) +
+  theme_minimal()
+
+```
 # Model

### 2024-02-15 outputs/paper/paper.qmd
updated

@@
 # Introduction
+Household income is defined as the gross income earned by all members in a household above 15 years of age (https://www.investopedia.com/terms/h/household_income.asp).
+Over the years, it has been debated whether household incomes at all affect one’s affiliation toward a political school of thought.
+It is a reasonable hypothesis to assume a sort of relationship between income and voting either Democrat or Republican, as both parties have different economic outlooks thereby affecting incomes differently.
+Presumably, a higher income inequality polarizes political leaning further.
+Therefore it is in our best interests to study whether the economically disadvantaged vote to improve their quality of life.
+
+In ‘Income Inequality and Partisan Voting in the United States’, Andrew Gelman, Lane Kenworthy and Yu-Sung Su (https://www.jstor.org/stable/42956457?seq=11) make a case for higher earning Americans voting Republican, whereas Jeff Madrick (https://www.nytimes.com/2020/07/31/books/review/the-system-robert-reich-break-em-up-zephyr-teachout.html) argues how working-class Americans voted supposedly against their interests in voting Republican.
+Conflicting theories have emerged, and we intend to tackle this issue at hand of whether different income brackets tend to vote differently.
 
@@
 #| label: fig-figure3
-#| fig-cap: ""
+#| fig-cap: "Number of Respondents who follow Donald Trump at different levels by Household Income"
 #| warning: false
@@
   geom_bar(position = 'stack', color = 'black', stat = 'count') +
-  labs(title = "Number of People Following Trump by Income Group",
-       x = "Follows Trump",
-       y = "Count") +
+  labs(x = "Follows Trump",
+       y = "Number of Responses") +
   scale_fill_manual(values = c(

### 2024-02-15 scripts/02-data_cleaning.R

@@ -16,8 +16,7 @@ cleaned_data <- cleaned_data %>%
   drop_na()
 
 
-view(cleaned_data)
-
+View(cleaned_data)
 #### Save data ####
 write_csv(cleaned_data, "outputs/data/analysis_data.csv")
 

### 2024-02-15 scripts/04-model.R

@@ -1,32 +1,30 @@
 #### Preamble ####
-# Purpose: Models... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
-# License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Purpose: Simple Regression model of following trump vy income controlled by race and politically invovled
+# Author: Gavin Crooks and Samarth Rajani
+# Date: 14 February 2024 
+# Contact: gavin.crooks@mail.utoronto.ca or samarth.rajani@mail.utoronto.ca
+# Pre-requisites: 01-download_data and 02-data_cleaning  or 00-simulate_data 
 
 
 #### Workspace setup ####
 library(tidyverse)
-library(rstanarm)
 
 #### Read data ####
-analysis_data <- read_csv("outputs/data/analysis_data.csv")
+cleaned_data <- read_csv("outputs/data/analysis_data.csv")
+
+# Convert categorical variables to factors
+# Code found from r bloggers
+# https://www.r-bloggers.com/2020/10/hack-how-to-convert-all-character-variables-to-factors/
+cleaned_data[sapply(cleaned_data, is.character)] <- lapply(cleaned_data[sapply(cleaned_data, is.character)], 
+                                                           as.factor)
+
+sapply(cleaned_data, class)
+
+
 
 ### Model data ####
-first_model <-
-  stan_glm(
-    formula = flying_time ~ length + width,
-    data = analysis_data,
-    family = gaussian(),
-    prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
-    prior_intercept = normal(location = 0, scale = 2.5, autoscale = TRUE),
-    prior_aux = exponential(rate = 1, autoscale = TRUE),
-    seed = 853
-  )
-
+model <- lm(factor(follow_trump) ~ factor(hhld_inc), cleaned_data)
+summary(model)
 
 #### Save model ####
 saveRDS(

### 2024-02-15 scripts/01-download_data.R
more updates

@@ -10,7 +10,6 @@
 #### Workspace setup ####
 library(haven)
 library(tidyverse)
-library(data.table)
 
 #### Download data ####
 ### Data can be downloaded from the URL below as file format does not allow it to be opened directly or from folder in repo 

### 2024-02-15 outputs/paper/paper.qmd
almost done

@@
   - Samarth Rajani
-thanks: "Code and data are available at: LINK.https://github.com/Crooksyyy/The-Effects-of-Social-Media"
+thanks: "Code and data are available at: LINK.https://github.com/Crooksyyy/The-Effects-of-Social-Media , Original data available https://www.openicpsr.org/openicpsr/project/112081/version/V1/view"
 date: today
@@
 
-# Introduction
-Household income is defined as the gross income earned by all members in a household above 15 years of age (https://www.investopedia.com/terms/h/household_income.asp).
-Over the years, it has been debated whether household incomes at all affect one’s affiliation toward a political school of thought.
+# Introduction {#intro}
+Household income is defined as the gross income earned by all members in a household above 15 years of age [@hhld].
+Over the years, it has been debated whether household incomes at all affect one’s affiliation towards a political school of thought.
 It is a reasonable hypothesis to assume a sort of relationship between income and voting either Democrat or Republican, as both parties have different economic outlooks thereby affecting incomes differently.
-Presumably, a higher income inequality polarizes political leaning further.
-Therefore it is in our best interests to study whether the economically disadvantaged vote to improve their quality of life.
+Maybe higher income inequality polarizes political leaning further.
+Therefore, it is in our best interests to study whether the poor vote to improve their quality of life.
 
-In ‘Income Inequality and Partisan Voting in the United States’, Andrew Gelman, Lane Kenworthy and Yu-Sung Su (https://www.jstor.org/stable/42956457?seq=11) make a case for higher earning Americans voting Republican, whereas Jeff Madrick (https://www.nytimes.com/2020/07/31/books/review/the-system-robert-reich-break-em-up-zephyr-teachout.html) argues how working-class Americans voted supposedly against their interests in voting Republican.
-Conflicting theories have emerged, and we intend to tackle this issue at hand of whether different income brackets tend to vote differently.
+In ‘Income Inequality and Partisan Voting in the United States’, Andrew Gelman, Lane Kenworthy and Yu-Sung Su [@lane] make a case for higher earning Americans voting Republican, whereas Jeff Madrick [@article] argues how working-class Americans voted against their interests in voting Republican.
+Conflicting theories have emerged, and we intend on tackling this issue at hand of whether different income brackets tend to vote differently.
 
-The introduction is self-contained and tells a reader everything they need to know including: 1) broader context to motivate; 2) some detail about what the paper is about; 3) a clear gap that needs to be filled; 4) what was done; 5) what was found; 6) why it is important; 7) the structure of the paper.
-A reader should be able to read only the introduction and know what was done, why, and what was found.
-Likely 3 or 4 paragraphs, or 10 per cent of total.
+Our data has been obtained from ‘The Welfare Effects of Social Media’ [@paper] .
+Our code is supported by the following packages [@citeR] [@tidy] [@her] [@knitr]
 
@@
 #| label: fig-figure2
-#| fig-cap: "How Closely People Follow Politics from Responses in a facebook ad"
+#| fig-cap: "How Closely People Follow Mr.Donald Trump from Responses in a facebook ad"
 #| warning: false
@@
 
-ggplot(cleaned_data, aes(x = "", fill = follow_politics)) +
+ggplot(cleaned_data, aes(x = "", fill = follow_trump)) +
   geom_bar() +
@@
 ```{r}
+#| label: fig-figure4
+#| fig-cap: "Number of Respondents who follow Donald Trump at different levels by Race"
+#| warning: false
+#| message: false
+#| echo: false
 # Parts of this code from R-charts
 #https://r-charts.com/part-whole/stacked-bar-chart-ggplot2/
-# Assisited by Chat GPT3.5 - view full chat in inputs/llms/usage.txt
+# Assisted by Chat GPT3.5 - view full chat in inputs/llms/usage.txt
 ggplot(cleaned_data, aes(x = follow_trump, fill = race)) +
@@
 ```
-# Model
+# Results
 
-simple regression of income and politics data controlling for race
+```{r}
+# Create a table of proportions
+income_follow_table <- table(cleaned_data$follow_trump, cleaned_data$income_group)
+income_proportions <- prop.table(income_follow_table, margin = 1) * 100
+
+table1 <- tibble(income_proportions, colnames(c("Income Group", "Follows Trump" )))
+show(table1)
+```
+
+This papers goal was to identify if lower income household voted against their own interest.
+To understand this relationship we used the variable for how closely a respondent follows Mr.
+Donald Trump as our measurement of subscription to Republican ideas.
+Using this measurement, we organized the proportion of individuals by income class to how closely they follow Mr.
+Donald Trump in @fig-figure3.
+This graph shows that a proportional amount of each income class follows Mr.
+Donald Trump at similar levels across all income levels.
+Specifically, we mean the percentage of individuals  follow Mr.
+Donald Trump at different levels is the same no matter the income class.
+This means we can not conclude that income class impacts how closely individuals follow Mr.
+Donald Trump, and therefor, cannot conclude that different income levels subscribe to republican ideas more than the other.
+
+To further our analysis we computed the same graph however organized by race not income @fig-figure4.
+This resulted in a similar result as race is proportional between all levels of following Mr.
+Donald Trump.
+Therefore, consistent across races at to following republican rhetoric.
+Again, this means the same percentage of people that follow Mr.
+Donald Trump at different levels is the same for each race.
+Obviously, this is more difficult to conclude for minorities as their representation within the data set is so small as stated in @sec-race_data
+
+Overall, the results of this analysis were inconclusive to measure how income impacts individuals propensity to follow republican rhetoric.
+There are many reasons this could be true and as stated in the @intro there are multiple schools of thought previously studies on the topic.
 

### 2024-02-15 outputs/paper/paper.tex
update again
almost done

--- 2024-02-15 outputs/paper/paper.tex
@@
 \title{Paper 2\thanks{Code and data are available at:
-LINK.https://github.com/Crooksyyy/The-Effects-of-Social-Media}}
+LINK.https://github.com/Crooksyyy/The-Effects-of-Social-Media , Original
+data available
+https://www.openicpsr.org/openicpsr/project/112081/version/V1/view}}
 \author{Gavin Crooks \and Samarth Rajani}
-\date{February 14, 2024}
+\date{February 15, 2024}
 
@@
 }
-\section{Introduction}\label{introduction}
+\section{Introduction}\label{intro}
 
-The introduction is self-contained and tells a reader everything they
-need to know including: 1) broader context to motivate; 2) some detail
-about what the paper is about; 3) a clear gap that needs to be filled;
-4) what was done; 5) what was found; 6) why it is important; 7) the
-structure of the paper. A reader should be able to read only the
-introduction and know what was done, why, and what was found. Likely 3
-or 4 paragraphs, or 10 per cent of total.
+Household income is defined as the gross income earned by all members in
+a household above 15 years of age (SCOTT 2024). Over the years, it has
+been debated whether household incomes at all affect one's affiliation
+towards a political school of thought. It is a reasonable hypothesis to
+assume a sort of relationship between income and voting either Democrat
+or Republican, as both parties have different economic outlooks thereby
+affecting incomes differently. Maybe higher income inequality polarizes
+political leaning further. Therefore, it is in our best interests to
+study whether the poor vote to improve their quality of life.
+
+In `Income Inequality and Partisan Voting in the United States', Andrew
+Gelman, Lane Kenworthy and Yu-Sung Su (Gelman, Kenworthy, and Su 2010)
+make a case for higher earning Americans voting Republican, whereas Jeff
+Madrick (\textbf{article?}) argues how working-class Americans voted
+against their interests in voting Republican. Conflicting theories have
+emerged, and we intend on tackling this issue at hand of whether
+different income brackets tend to vote differently.
+
+Our data has been obtained from `The Welfare Effects of Social Media'
+(\textbf{paper?}) . Our code is supported by the following packages (R
+Core Team 2022) (Wickham et al. 2019) (\textbf{her?}) (Xie 2023)
 
@@
 
-\caption{\label{fig-figure2}How Closely People Follow Politics from
-Responses in a facebook ad}
+\caption{\label{fig-figure2}How Closely People Follow Mr.Donald Trump
+from Responses in a facebook ad}
 
@@
 
+\begin{figure}
+
+\centering{
+
+\includegraphics{paper_files/figure-pdf/fig-figure4-1.pdf}
+
+}
+
+\caption{\label{fig-figure4}Number of Respondents who follow Donald
+Trump at different levels by Race}
+
+\end{figure}%
+
+\begin{figure}
+
+\centering{
+
+\includegraphics{paper_files/figure-pdf/fig-figure3-1.pdf}
+
+}
+
+\caption{\label{fig-figure3}Number of Respondents who follow Donald
+Trump at different levels by Household Income}
+
+\end{figure}%
+
+\section{Results}\label{results}
+
 \begin{Shaded}
 \begin{Highlighting}[]
-\CommentTok{\# Parts of this code from R{-}charts}
-\CommentTok{\#https://r{-}charts.com/part{-}whole/stacked{-}bar{-}chart{-}ggplot2/}
-\FunctionTok{ggplot}\NormalTok{(cleaned\_data, }\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ follow\_trump, }\AttributeTok{fill =}\NormalTok{ race)) }\SpecialCharTok{+}
-  \FunctionTok{geom\_bar}\NormalTok{(}\AttributeTok{position =} \StringTok{\textquotesingle{}stack\textquotesingle{}}\NormalTok{, }\AttributeTok{color =} \StringTok{\textquotesingle{}black\textquotesingle{}}\NormalTok{, }\AttributeTok{stat =} \StringTok{\textquotesingle{}count\textquotesingle{}}\NormalTok{) }\SpecialCharTok{+}
-  \FunctionTok{labs}\NormalTok{(}\AttributeTok{title =} \StringTok{"Number of People Following Trump by Race"}\NormalTok{,}
-       \AttributeTok{x =} \StringTok{"Follows Trump"}\NormalTok{,}
-       \AttributeTok{y =} \StringTok{"Count"}\NormalTok{) }\SpecialCharTok{+}
-  \FunctionTok{scale\_fill\_manual}\NormalTok{(}\AttributeTok{values =} \FunctionTok{c}\NormalTok{(}\StringTok{\textquotesingle{}White / Caucasian\textquotesingle{}} \OtherTok{=} \StringTok{\textquotesingle{}lightblue\textquotesingle{}}\NormalTok{, }\StringTok{\textquotesingle{}Black or African American\textquotesingle{}} \OtherTok{=} \StringTok{\textquotesingle{}lightcoral\textquotesingle{}}\NormalTok{, }\StringTok{\textquotesingle{}Asian or Pacific Islander\textquotesingle{}} \OtherTok{=} \StringTok{\textquotesingle{}lightgreen\textquotesingle{}}\NormalTok{, }\StringTok{\textquotesingle{}Hispanic\textquotesingle{}} \OtherTok{=} \StringTok{\textquotesingle{}plum\textquotesingle{}}\NormalTok{,}
-                               \StringTok{\textquotesingle{}Other  (please specify)\textquotesingle{}} \OtherTok{=} \StringTok{\textquotesingle{}lightgoldenrodyellow\textquotesingle{}}\NormalTok{)) }\SpecialCharTok{+}
-  \FunctionTok{theme\_minimal}\NormalTok{()}
+\CommentTok{\# Create a table of proportions}
+\NormalTok{income\_follow\_table }\OtherTok{\textless{}{-}} \FunctionTok{table}\NormalTok{(cleaned\_data}\SpecialCharTok{$}\NormalTok{follow\_trump, cleaned\_data}\SpecialCharTok{$}\NormalTok{income\_group)}
+\NormalTok{income\_proportions }\OtherTok{\textless{}{-}} \FunctionTok{prop.table}\NormalTok{(income\_follow\_table, }\AttributeTok{margin =} \DecValTok{1}\NormalTok{) }\SpecialCharTok{*} \DecValTok{100}
+
+\NormalTok{table1 }\OtherTok{\textless{}{-}} \FunctionTok{tibble}\NormalTok{(income\_proportions, }\FunctionTok{colnames}\NormalTok{(}\FunctionTok{c}\NormalTok{(}\StringTok{"Income Group"}\NormalTok{, }\StringTok{"Follows Trump"}\NormalTok{ )))}
+\FunctionTok{show}\NormalTok{(table1)}
 \end{Highlighting}
@@
 
-\includegraphics{paper_files/figure-pdf/unnamed-chunk-5-1.pdf}
+\begin{verbatim}
+# A tibble: 4 x 1
+  income_proportions[,"$0 to $19,9~1 [,"$100,000 and up"] [,"$20,000 to $49,99~2
+                               <dbl>                <dbl>                  <dbl>
+1                               9.12                 16.9                   28.1
+2                               5.86                 22.5                   29.0
+3                               7.57                 20.2                   29.3
+4                               6.73                 22.4                   25.3
+# i abbreviated names: 1: income_proportions[,"$0 to $19,999"],
+#   2: [,"$20,000 to $49,999"]
+# i 1 more variable: income_proportions[4:5] <dbl>
+\end{verbatim}
 
-\section{Model}\label{model}
+This papers goal was to identify if lower income household voted against
+their own interest. To understand this relationship we used the variable
+for how closely a respondent follows Mr.~Donald Trump as our measurement
+of subscription to Republican ideas. Using this measurement, we
+organized the proportion of individuals by income class to how closely
+they follow Mr.~Donald Trump in Figure~\ref{fig-figure3}. This graph
+shows that a proportional amount of each income class follows Mr.~Donald
+Trump at similar levels across all income levels. Specifically, we mean
+the percentage of individuals follow Mr.~Donald Trump at different
+levels is the same no matter the income class. This means we can not
+conclude that income class impacts how closely individuals follow
+Mr.~Donald Trump, and therefor, cannot conclude that different income
+levels subscribe to republican ideas more than the other.
 
-simple regression of income and politics data controlling for race
+To further our analysis we computed the same graph however organized by
+race not income Figure~\ref{fig-figure4}. This resulted in a similar
+result as race is proportional between all levels of following
+Mr.~Donald Trump. Therefore, consistent across races at to following
+republican rhetoric. Again, this means the same percentage of people
+that follow Mr.~Donald Trump at different levels is the same for each
+race. Obviously, this is more difficult to conclude for minorities as
+their representation within the data set is so small as stated in
+Section~\ref{sec-race_data}
+
+Overall, the results of this analysis were inconclusive to measure how
+income impacts individuals propensity to follow republican rhetoric.
+There are many reasons this could be true and as stated in the
+(\textbf{intro?}) there are multiple schools of thought previously
+studies on the topic.
 
@@
 \begin{CSLReferences}{1}{0}
-\bibitem[\citeproctext]{ref-citeLahman}
-Friendly, Michael, Chris Dalzell, Martin Monkman, and Dennis Murphy.
-2020. \emph{Lahman: Sean {``Lahman''} Baseball Database}.
-\url{https://CRAN.R-project.org/package=Lahman}.
+\bibitem[\citeproctext]{ref-10.1257ux2faer.20190658}
+Allcott, Hunt, Luca Braghieri, Sarah Eichmeyer, and Matthew Gentzkow.
+2020. {``The Welfare Effects of Social Media.''} \emph{American Economic
+Review}. \url{https://doi.org/10.1257/aer.20190658}.
 
-\bibitem[\citeproctext]{ref-gebru2021datasheets}
-Gebru, Timnit, Jamie Morgenstern, Briana Vecchione, Jennifer Wortman
-Vaughan, Hanna Wallach, Hal Daumé Iii, and Kate Crawford. 2021.
-{``Datasheets for Datasets.''} \emph{Communications of the ACM} 64 (12):
-86--92.
+\bibitem[\citeproctext]{ref-lane}
+Gelman, Andrew, Lane Kenworthy, and Yu-Sung Su. 2010. {``Income
+Inequality and Partisan Voting in the United States.''} \emph{Social
+Science Quarterly}. {[}University of Texas Press, Wiley{]}.
+\url{http://www.jstor.org/stable/42956457}.
 
-\bibitem[\citeproctext]{ref-rstanarm}
-Goodrich, Ben, Jonah Gabry, Imad Ali, and Sam Brilleman. 2022.
-{``Rstanarm: {Bayesian} Applied Regression Modeling via {Stan}.''}
-\url{https://mc-stan.org/rstanarm/}.
+\bibitem[\citeproctext]{ref-Madrick_2020}
+Madrick, Jeff. 2020. {``Why the Working Class Votes Against Its Economic
+Interests.''} \emph{The New York Times}, July.
+\url{https://www.nytimes.com/2020/07/31/books/review/the-system-robert-reich-break-em-up-zephyr-teachout.html}.
 
-\bibitem[\citeproctext]{ref-palmerpenguins}
-Horst, Allison Marie, Alison Presmanes Hill, and Kristen B Gorman. 2020.
-\emph{Palmerpenguins: Palmer Archipelago (Antarctica) Penguin Data}.
-\url{https://doi.org/10.5281/zenodo.3960218}.
+\bibitem[\citeproctext]{ref-here}
+Müller, Kirill. 2020. {``Here: A Simpler Way to Find Your Files.''}
+\url{https://CRAN.R-project.org/package=here}.
 
@@
 
-\bibitem[\citeproctext]{ref-thereferencecanbewhatever}
+\bibitem[\citeproctext]{ref-hhld}
+SCOTT, MICHELLE P. 2024. {``Household Income.''} investopedia.
+\url{https://www.investopedia.com/terms/h/household_income.asp}.
+
+\bibitem[\citeproctext]{ref-tidy}
 Wickham, Hadley, Mara Averick, Jennifer Bryan, Winston Chang, Lucy
 D'Agostino McGowan, Romain François, Garrett Grolemund, et al. 2019.
-{``Welcome to the {tidyverse}.''} \emph{Journal of Open Source Software}
-4 (43): 1686. \url{https://doi.org/10.21105/joss.01686}.
+{``Welcome to the {tidyverse}.''} \emph{Journal of Open Source
+Software}. \url{https://doi.org/10.21105/joss.01686}.
+
+\bibitem[\citeproctext]{ref-knitr}
+Xie, Yihui. 2023. {``Knitr: A General-Purpose Package for Dynamic Report
+Generation in r.''} \url{https://yihui.org/knitr/}.
 

### 2024-02-15 outputs/paper/paper.qmd
update

@@
 library(knitr)
-cleaned_data <- read_csv(here::here("outputs/Data/analysis_data.csv"))
+cleaned_data <- read_csv(here::here("outputs/data/analysis_data.csv"))
 
@@
 
-# Introduction {#intro}
+# Introduction {#sec-intro}
 Household income is defined as the gross income earned by all members in a household above 15 years of age [@hhld].
@@
 
-In ‘Income Inequality and Partisan Voting in the United States’, Andrew Gelman, Lane Kenworthy and Yu-Sung Su [@lane] make a case for higher earning Americans voting Republican, whereas Jeff Madrick [@article] argues how working-class Americans voted against their interests in voting Republican.
+In ‘Income Inequality and Partisan Voting in the United States’, Andrew Gelman, Lane Kenworthy and Yu-Sung Su [@lane] make a case for higher earning Americans voting Republican, whereas Jeff Madrick [@Madrick_2020] argues how working-class Americans voted against their interests in voting Republican.
 Conflicting theories have emerged, and we intend on tackling this issue at hand of whether different income brackets tend to vote differently.
+
+The remainder of this paper is structured as follows.
+@sec-data will intorduce the data set and the variables it contains.
+@sec-results will display the findings of our data in relation to our paper.
+@sec-data focuses on the strength and weaknesses of our paper.
 
@@
 ## Data Introduction {#sec-dataintro}
-The data used in this paper is from (cite og paper).
-The data used in the paper is extremely complicated as it combines numerous data sets to complete their analysis.
-In this paper, we wanted to simplify the data to determine if their paper had underlying biases within the data.
-To do this we focused on one of their eleven data sets, baseline dataset as it was the most comprehensive.
-This data was collected through a facebook ad.
-The respondents answered a number of questions including questions about income, ethnicity, family, political beliefs and political following.
-THis is a very useful data set outside the scope of the original paper as it can be analyzed to answer a number of questions.
-The data set was cleaned to focus on respondents income, race and how closely they follow politics.
-This provided a data set of approximately 6000 complete responses after removing unfinished responses.
-This was a substantial decrease from the orignal 24000 responses in the data.
+
+The data for this paper was collected from the replication package of the paper ‘The Welfare Effects of Social Media’[@paper] The authors from that data had collected this data themselves using an online survey platform called Qulatrics, inquiring about personal information such as personal names, IP addresses, extent of by which the subjects follow politics, etc.
+Notably the dataset would contain a lot of confidential information, that if released in the replication package would cause ethical problems.
+As a result, the authors included the de-identified versions of their data collected, which was used in our analysis too.
 
 ## Income Data {#sec-income_data}
-The variable within the data was the income variable.
-The questionnaire included a categorical value for the the household income of respondents.
-The data can be visualized in @figure1.
-This graph illustrates that the least number of households make greater than 100,000 USD, below 20,000USD or preferred not to answer.
-This graph also shows what the categorical option were for the respondents to the questionnaire.
-@figure1 closely resembles the expected distribution of USA household income.
-As expected in any income distribution the majority of responses fall within the average income ranges of the USA, between 20,000USD and 100,000USD.
-These factors indicate that the data set has an accurate representation of household income.
+
+Our key variables of interest include household income.
+The survey participants were offered options in bins starting at 0 to 9,999 US dollar range, with every succeeding bin also being 9,999 USD wide.
+The bins went up to a ceiling of 50,000 USD per annum, then every next bin was 25,000 USD wide until a ceiling of 150,000 USD.
+In our analysis we combine the bins above 9,999 into – 20,000 to 49,999, 50,000 to 99,999 and the rest being 100,000 and up.
+The option of ‘Prefer not to answer’ was also available, and the entries with that response were dropped.
+The distribution of the data can be seen in @fig-figure1 .
+
 ```{r}
@@
 ```
+
+## Politics Data {#sec-pol_data}
+
+Another variable of use is the extent to which the subjects follow Mr.
+Donald Trump, leader of the Republican Party.
+The possible responses were ‘Not at all closely', 'Somewhat closely,’ ‘Rather closely’ and ‘Very Closely,’ and the respondents could select one of these options which will become our measure of measuring subscription to Republican ideas.
+This data is represented using a pie chart in @fig-figure2.
+
+```{r}
+#| label: fig-figure2
+#| fig-cap: "How Closely People Follow Mr.Donald Trump from Responses in a facebook ad"
+#| warning: false
+#| message: false
+#| echo: false
+
+ggplot(cleaned_data, aes(x = "", fill = follow_trump)) +
+  geom_bar() +
+  coord_polar("y") +
+  labs(fill = "Legend") +
+  theme(axis.title = element_blank())
+
+```
+
 ## Ethnicity Data {#sec-race_data}
-The second question of the data that we have included in our analysis is the ethnicity of the respondents.
-This again is a categorical variable, that the individual self identifies their own ethnicity.
-The response options included Asian or Pacific Islander, White / Caucasian, Hispanic, Black or African American and other.
-@race_dist shows the percentage of respondents in each  with the overwhelming majority of responses being Caucasian at nearly 70%.
-This is actually less than the most recent estimates by the United States government which estimate over 75% of the population is Caucasian (cite us gov).
-The data also has an over representation of Asian and Native Americans.
-This results in an under representation of Hispanic and African American populations.
-
-https://www.census.gov/quickfacts/fact/table/US/PST045222
 
@@
 
-## Politics Data {#sec-pol_data}
+# Results {#sec-results}
 
-The third variable in the data that is included in our analysis is a variable of respondents self identifying how closely they follow politics.
-This is another categorical variable measured as Not at all closely, Somewhat closely, Rather closely and  Very closely.
-This variable faces many problems as this categorical scale is not consistent across respondents.
-To be specific we mean someone who identifies as someone who does follows Not at all closely can be following politics more than someone who identifies as Somewhat closely.
-This is a measurement issue within to the questions asked in the survey and all self identifying variables in general.
-@figure2 shows the quantity of respondents in each group.
-The most common response is that they follow somewhat closely and the other responses are relatively even.
-```{r}
-#| label: fig-figure2
-#| fig-cap: "How Closely People Follow Mr.Donald Trump from Responses in a facebook ad"
-#| warning: false
-#| message: false
-#| echo: false
+This papers goal was to identify if lower income household voted against their own interest.
+To understand this relationship we used the variable for how closely a respondent follows Mr.
+Donald Trump as our measurement of subscription to Republican ideas.
+Using this measurement, we organized the proportion of individuals by income class to how closely they follow Mr.
+Donald Trump in @fig-figure3.
+This graph shows that a proportional amount of each income class follows Mr.
+Donald Trump at similar levels across all income levels.
+Specifically, we mean the percentage of individuals  follow Mr.
+Donald Trump at different levels is the same no matter the income class.
+This means we can not conclude that income class impacts how closely individuals follow Mr.
+Donald Trump, and therefor, cannot conclude that different income levels subscribe to republican ideas more than the other.
 
-ggplot(cleaned_data, aes(x = "", fill = follow_trump)) +
-  geom_bar() +
-  coord_polar("y") +
-  labs(fill = "Legend") +
-  theme(axis.title = element_blank())
-
-```
-## Missing Data {#sec-Missing_data}
-
-```{r}
-#| label: fig-figure4
-#| fig-cap: "Number of Respondents who follow Donald Trump at different levels by Race"
-#| warning: false
-#| message: false
-#| echo: false
-# Parts of this code from R-charts
-#https://r-charts.com/part-whole/stacked-bar-chart-ggplot2/
-# Assisted by Chat GPT3.5 - view full chat in inputs/llms/usage.txt
-ggplot(cleaned_data, aes(x = follow_trump, fill = race)) +
-  geom_bar(position = 'stack', color = 'black', stat = 'count') +
-  labs(title = "Number of People Following Trump by Race",
-       x = "Follows Trump",
-       y = "Count") +
-  scale_fill_manual(values = c('White / Caucasian' = 'lightblue', 'Black or African American' = 'lightcoral', 'Asian or Pacific Islander' = 'lightgreen', 'Hispanic' = 'plum',
-                               'Other  (please specify)' = 'lightgoldenrodyellow')) +
-  theme_minimal()
-
-```
 ```{r}
@@
 ```
-# Results
-
-```{r}
-# Create a table of proportions
-income_follow_table <- table(cleaned_data$follow_trump, cleaned_data$income_group)
-income_proportions <- prop.table(income_follow_table, margin = 1) * 100
-
-table1 <- tibble(income_proportions, colnames(c("Income Group", "Follows Trump" )))
-show(table1)
-```
-
-This papers goal was to identify if lower income household voted against their own interest.
-To understand this relationship we used the variable for how closely a respondent follows Mr.
-Donald Trump as our measurement of subscription to Republican ideas.
-Using this measurement, we organized the proportion of individuals by income class to how closely they follow Mr.
-Donald Trump in @fig-figure3.
-This graph shows that a proportional amount of each income class follows Mr.
-Donald Trump at similar levels across all income levels.
-Specifically, we mean the percentage of individuals  follow Mr.
-Donald Trump at different levels is the same no matter the income class.
-This means we can not conclude that income class impacts how closely individuals follow Mr.
-Donald Trump, and therefor, cannot conclude that different income levels subscribe to republican ideas more than the other.
 
@@
 
+```{r}
+#| label: fig-figure4
+#| fig-cap: "Number of Respondents who follow Donald Trump at different levels by Race"
+#| warning: false
+#| message: false
+#| echo: false
+# Parts of this code from R-charts
+#https://r-charts.com/part-whole/stacked-bar-chart-ggplot2/
+# Assisted by Chat GPT3.5 - view full chat in inputs/llms/usage.txt
+ggplot(cleaned_data, aes(x = follow_trump, fill = race)) +
+  geom_bar(position = 'stack', color = 'black', stat = 'count') +
+  labs(title = "Number of People Following Trump by Race",
+       x = "Follows Trump",
+       y = "Count") +
+  scale_fill_manual(values = c('White / Caucasian' = 'lightblue', 'Black or African American' = 'lightcoral', 'Asian or Pacific Islander' = 'lightgreen', 'Hispanic' = 'plum',
+                               'Other  (please specify)' = 'lightgoldenrodyellow')) +
+  theme_minimal()
+
+```
+
 Overall, the results of this analysis were inconclusive to measure how income impacts individuals propensity to follow republican rhetoric.
-There are many reasons this could be true and as stated in the @intro there are multiple schools of thought previously studies on the topic.
-
-# Discussion
-like to incluse variables like state etc data set too small/ incomplete for that
-## First discussion point {#sec-first-point}
-
-If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.
-
-## Second discussion point
-
-## Third discussion point
-
-## Weaknesses and next steps
-
-Weaknesses and next steps should also be included.
-
-\newpage
-
-\appendix
-
-# Appendix {-}
-
-# Additional data details
-
-# Model details {#sec-model-details}
+There are many reasons this could be true and as stated in the @sec-intro there are multiple schools of thought previously studies on the topic.
 

### 2024-02-15 outputs/paper/paper.tex
update

@@
 \fi
-
-\usepackage{color}
-\usepackage{fancyvrb}
-\newcommand{\VerbBar}{|}
-\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
-\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
-% Add ',fontsize=\small' for more characters per line
-\usepackage{framed}
-\definecolor{shadecolor}{RGB}{241,243,245}
-\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
-\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
-\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
-\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.40,0.45,0.13}{#1}}
-\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
-\newcommand{\BuiltInTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
-\newcommand{\CharTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
-\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
-\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{\textit{#1}}}
-\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
-\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
-\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
-\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
-\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{\textit{#1}}}
-\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
-\newcommand{\ExtensionTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
-\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
-\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.28,0.35,0.67}{#1}}
-\newcommand{\ImportTok}[1]{\textcolor[rgb]{0.00,0.46,0.62}{#1}}
-\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
-\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
-\newcommand{\NormalTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
-\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
-\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
-\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
-\newcommand{\RegionMarkerTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
-\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
-\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
-\newcommand{\StringTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
-\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.07,0.07,0.07}{#1}}
-\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
-\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{\textit{#1}}}
 
@@
 }
-\section{Introduction}\label{intro}
+\section{Introduction}\label{sec-intro}
 
@@
 make a case for higher earning Americans voting Republican, whereas Jeff
-Madrick (\textbf{article?}) argues how working-class Americans voted
-against their interests in voting Republican. Conflicting theories have
-emerged, and we intend on tackling this issue at hand of whether
-different income brackets tend to vote differently.
+Madrick (Madrick 2020) argues how working-class Americans voted against
+their interests in voting Republican. Conflicting theories have emerged,
+and we intend on tackling this issue at hand of whether different income
+brackets tend to vote differently.
+
+The remainder of this paper is structured as follows.
+Section~\ref{sec-data} will intorduce the data set and the variables it
+contains. Section~\ref{sec-results} will display the findings of our
+data in relation to our paper. Section~\ref{sec-data} focuses on the
+strength and weaknesses of our paper.
 
 Our data has been obtained from `The Welfare Effects of Social Media'
-(\textbf{paper?}) . Our code is supported by the following packages (R
-Core Team 2022) (Wickham et al. 2019) (\textbf{her?}) (Xie 2023)
+(Allcott et al. 2020) . Our code is supported by the following packages
+(R Core Team 2022) (Wickham et al. 2019) (Müller 2020) (Xie 2023)
 
@@
 
-The data used in this paper is from (cite og paper). The data used in
-the paper is extremely complicated as it combines numerous data sets to
-complete their analysis. In this paper, we wanted to simplify the data
-to determine if their paper had underlying biases within the data. To do
-this we focused on one of their eleven data sets, baseline dataset as it
-was the most comprehensive. This data was collected through a facebook
-ad. The respondents answered a number of questions including questions
-about income, ethnicity, family, political beliefs and political
-following. THis is a very useful data set outside the scope of the
-original paper as it can be analyzed to answer a number of questions.
-The data set was cleaned to focus on respondents income, race and how
-closely they follow politics. This provided a data set of approximately
-6000 complete responses after removing unfinished responses. This was a
-substantial decrease from the orignal 24000 responses in the data.
+The data for this paper was collected from the replication package of
+the paper `The Welfare Effects of Social Media'(Allcott et al. 2020) The
+authors from that data had collected this data themselves using an
+online survey platform called Qulatrics, inquiring about personal
+information such as personal names, IP addresses, extent of by which the
+subjects follow politics, etc. Notably the dataset would contain a lot
+of confidential information, that if released in the replication package
+would cause ethical problems. As a result, the authors included the
+de-identified versions of their data collected, which was used in our
+analysis too.
 
@@
 
-The variable within the data was the income variable. The questionnaire
-included a categorical value for the the household income of
-respondents. The data can be visualized in (\textbf{figure1?}). This
-graph illustrates that the least number of households make greater than
-100,000 USD, below 20,000USD or preferred not to answer. This graph also
-shows what the categorical option were for the respondents to the
-questionnaire. (\textbf{figure1?}) closely resembles the expected
-distribution of USA household income. As expected in any income
-distribution the majority of responses fall within the average income
-ranges of the USA, between 20,000USD and 100,000USD. These factors
-indicate that the data set has an accurate representation of household
-income.
+Our key variables of interest include household income. The survey
+participants were offered options in bins starting at 0 to 9,999 US
+dollar range, with every succeeding bin also being 9,999 USD wide. The
+bins went up to a ceiling of 50,000 USD per annum, then every next bin
+was 25,000 USD wide until a ceiling of 150,000 USD. In our analysis we
+combine the bins above 9,999 into -- 20,000 to 49,999, 50,000 to 99,999
+and the rest being 100,000 and up. The option of `Prefer not to answer'
+was also available, and the entries with that response were dropped. The
+distribution of the data can be seen in Figure~\ref{fig-figure1} .
 
@@
 
+\subsection{Politics Data}\label{sec-pol_data}
+
+Another variable of use is the extent to which the subjects follow
+Mr.~Donald Trump, leader of the Republican Party. The possible responses
+were `Not at all closely', `Somewhat closely,' `Rather closely' and
+`Very Closely,' and the respondents could select one of these options
+which will become our measure of measuring subscription to Republican
+ideas. This data is represented using a pie chart in
+Figure~\ref{fig-figure2}.
+
+\begin{figure}
+
+\centering{
+
+\includegraphics{paper_files/figure-pdf/fig-figure2-1.pdf}
+
+}
+
+\caption{\label{fig-figure2}How Closely People Follow Mr.Donald Trump
+from Responses in a facebook ad}
+
+\end{figure}%
+
 \subsection{Ethnicity Data}\label{sec-race_data}
-
-The second question of the data that we have included in our analysis is
-the ethnicity of the respondents. This again is a categorical variable,
-that the individual self identifies their own ethnicity. The response
-options included Asian or Pacific Islander, White / Caucasian, Hispanic,
-Black or African American and other. (\textbf{race\_dist?}) shows the
-percentage of respondents in each with the overwhelming majority of
-responses being Caucasian at nearly 70\%. This is actually less than the
-most recent estimates by the United States government which estimate
-over 75\% of the population is Caucasian (cite us gov). The data also
-has an over representation of Asian and Native Americans. This results
-in an under representation of Hispanic and African American populations.
-
-https://www.census.gov/quickfacts/fact/table/US/PST045222
 
@@
 
-\subsection{Politics Data}\label{sec-pol_data}
-
-The third variable in the data that is included in our analysis is a
-variable of respondents self identifying how closely they follow
-politics. This is another categorical variable measured as Not at all
-closely, Somewhat closely, Rather closely and Very closely. This
-variable faces many problems as this categorical scale is not consistent
-across respondents. To be specific we mean someone who identifies as
-someone who does follows Not at all closely can be following politics
-more than someone who identifies as Somewhat closely. This is a
-measurement issue within to the questions asked in the survey and all
-self identifying variables in general. (\textbf{figure2?}) shows the
-quantity of respondents in each group. The most common response is that
-they follow somewhat closely and the other responses are relatively
-even.
-
-\begin{figure}
-
-\centering{
-
-\includegraphics{paper_files/figure-pdf/fig-figure2-1.pdf}
-
-}
-
-\caption{\label{fig-figure2}How Closely People Follow Mr.Donald Trump
-from Responses in a facebook ad}
-
-\end{figure}%
-
-\subsection{Missing Data}\label{sec-Missing_data}
-
-\begin{figure}
-
-\centering{
-
-\includegraphics{paper_files/figure-pdf/fig-figure4-1.pdf}
-
-}
-
-\caption{\label{fig-figure4}Number of Respondents who follow Donald
-Trump at different levels by Race}
-
-\end{figure}%
-
-\begin{figure}
-
-\centering{
-
-\includegraphics{paper_files/figure-pdf/fig-figure3-1.pdf}
-
-}
-
-\caption{\label{fig-figure3}Number of Respondents who follow Donald
-Trump at different levels by Household Income}
-
-\end{figure}%
-
-\section{Results}\label{results}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{\# Create a table of proportions}
-\NormalTok{income\_follow\_table }\OtherTok{\textless{}{-}} \FunctionTok{table}\NormalTok{(cleaned\_data}\SpecialCharTok{$}\NormalTok{follow\_trump, cleaned\_data}\SpecialCharTok{$}\NormalTok{income\_group)}
-\NormalTok{income\_proportions }\OtherTok{\textless{}{-}} \FunctionTok{prop.table}\NormalTok{(income\_follow\_table, }\AttributeTok{margin =} \DecValTok{1}\NormalTok{) }\SpecialCharTok{*} \DecValTok{100}
-
-\NormalTok{table1 }\OtherTok{\textless{}{-}} \FunctionTok{tibble}\NormalTok{(income\_proportions, }\FunctionTok{colnames}\NormalTok{(}\FunctionTok{c}\NormalTok{(}\StringTok{"Income Group"}\NormalTok{, }\StringTok{"Follows Trump"}\NormalTok{ )))}
-\FunctionTok{show}\NormalTok{(table1)}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-# A tibble: 4 x 1
-  income_proportions[,"$0 to $19,9~1 [,"$100,000 and up"] [,"$20,000 to $49,99~2
-                               <dbl>                <dbl>                  <dbl>
-1                               9.12                 16.9                   28.1
-2                               5.86                 22.5                   29.0
-3                               7.57                 20.2                   29.3
-4                               6.73                 22.4                   25.3
-# i abbreviated names: 1: income_proportions[,"$0 to $19,999"],
-#   2: [,"$20,000 to $49,999"]
-# i 1 more variable: income_proportions[4:5] <dbl>
-\end{verbatim}
+\section{Results}\label{sec-results}
 
@@
 
+\begin{figure}
+
+\centering{
+
+\includegraphics{paper_files/figure-pdf/fig-figure3-1.pdf}
+
+}
+
+\caption{\label{fig-figure3}Number of Respondents who follow Donald
+Trump at different levels by Household Income}
+
+\end{figure}%
+
 To further our analysis we computed the same graph however organized by
@@
 
+\begin{figure}
+
+\centering{
+
+\includegraphics{paper_files/figure-pdf/fig-figure4-1.pdf}
+
+}
+
+\caption{\label{fig-figure4}Number of Respondents who follow Donald
+Trump at different levels by Race}
+
+\end{figure}%
+
 Overall, the results of this analysis were inconclusive to measure how
@@
 There are many reasons this could be true and as stated in the
-(\textbf{intro?}) there are multiple schools of thought previously
+Section~\ref{sec-intro} there are multiple schools of thought previously
 studies on the topic.
-
-\section{Discussion}\label{discussion}
-
-like to incluse variables like state etc data set too small/ incomplete
-for that \#\# First discussion point \{\#sec-first-point\}
-
-If my paper were 10 pages, then should be be at least 2.5 pages. The
-discussion is a chance to show off what you know and what you learnt
-from all this.
-
-\subsection{Second discussion point}\label{second-discussion-point}
-
-\subsection{Third discussion point}\label{third-discussion-point}
-
-\subsection{Weaknesses and next steps}\label{weaknesses-and-next-steps}
-
-Weaknesses and next steps should also be included.
-
-\newpage
-
-\appendix
-
-\section*{Appendix}\label{appendix}
-\addcontentsline{toc}{section}{Appendix}
-
-\section{Additional data details}\label{additional-data-details}
-
-\section{Model details}\label{sec-model-details}
 
@@
 \begin{CSLReferences}{1}{0}
-\bibitem[\citeproctext]{ref-10.1257ux2faer.20190658}
+\bibitem[\citeproctext]{ref-paper}
 Allcott, Hunt, Luca Braghieri, Sarah Eichmeyer, and Matthew Gentzkow.
@@
 
-\bibitem[\citeproctext]{ref-here}
+\bibitem[\citeproctext]{ref-her}
 Müller, Kirill. 2020. {``Here: A Simpler Way to Find Your Files.''}

### 2024-02-15 outputs/paper/paper.qmd
update

@@
   - Samarth Rajani
-thanks: "Code and data are available at: LINK.https://github.com/Crooksyyy/The-Effects-of-Social-Media , Original data available https://www.openicpsr.org/openicpsr/project/112081/version/V1/view"
+thanks: "Code and data are available at: LINK.https://github.com/Crooksyyy/The-Effects-of-Social-Media"
 date: today
@@
 bibliography: references.bib
-nocite: |
-  @*
+
 ---
@@
   )) +
-  theme_minimal()
+  theme_minimal() +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1))
 
@@
   geom_bar(position = 'stack', color = 'black', stat = 'count') +
-  labs(title = "Number of People Following Trump by Race",
-       x = "Follows Trump",
+  labs(x = "Follows Trump",
        y = "Count") +
@@
                                'Other  (please specify)' = 'lightgoldenrodyellow')) +
-  theme_minimal()
+  theme_minimal() +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1))
 

### 2024-02-15 outputs/paper/paper.tex
update

@@
 \title{Paper 2\thanks{Code and data are available at:
-LINK.https://github.com/Crooksyyy/The-Effects-of-Social-Media , Original
-data available
-https://www.openicpsr.org/openicpsr/project/112081/version/V1/view}}
+LINK.https://github.com/Crooksyyy/The-Effects-of-Social-Media}}
 \author{Gavin Crooks \and Samarth Rajani}

### 2024-02-15 scripts/02-data_cleaning.R
Almost done

@@ -15,7 +15,6 @@ cleaned_data <- select(raw_data, hhld_inc, race, follow_politics, follow_trump)
 cleaned_data <- cleaned_data %>% 
   drop_na()
 
-
 View(cleaned_data)
 #### Save data ####
 write_csv(cleaned_data, "outputs/data/analysis_data.csv")

### 2024-02-15 outputs/paper/paper.qmd
updates

@@
 ---
-title: "Paper 2"
+title: "How Household Income Impacts Political Views, Focusing on Mr. Donald Trump, Yielded Inconclusive Results"
 author: 
@@
 date-format: long
-abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
+abstract: "This study explores the relationship between household income, ethnicity, and political preferences using data from 'The Welfare Effects of Social Media.' Despite inconclusive findings challenging the presumed impact of income on political views, our innovative metric, measuring respondents' propensity to follow Donald Trump, did not provide conclusive results.
+This introduces new avenues in political science and statistics, encouraging further exploration into understanding the dynamics of these relationships.
+The study contributes to the ongoing discourse on the complex relationships between income, ethnicity, and political inclinations."
 format: pdf
@@
 Conflicting theories have emerged, and we intend on tackling this issue at hand of whether different income brackets tend to vote differently.
+By measuring the difference in propensity to follow Mr.
+Donald Trump in relation to household income.
 
 The remainder of this paper is structured as follows.
-@sec-data will intorduce the data set and the variables it contains.
+@sec-data will introduce the data set and the variables it contains.
 @sec-results will display the findings of our data in relation to our paper.
-@sec-data focuses on the strength and weaknesses of our paper.
+The @sec-disc will discuss why the findings matter and the weaknesses of our analysis.
 
@@
 The option of ‘Prefer not to answer’ was also available, and the entries with that response were dropped.
-The distribution of the data can be seen in @fig-figure1 .
-
-```{r}
-#| label: fig-figure1
-#| fig-cap: "Distribution of Income from Responses in a facebook ad"
-#| warning: false
-#| message: false
-#| echo: false
-
-ggplot(cleaned_data, aes(x = reorder(hhld_inc, -table(hhld_inc)[hhld_inc]), fill = hhld_inc)) +
-  geom_bar() +
-  labs(x = "Household Income",
-       y = "Number of Respondents") +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
-  guides(fill = FALSE) # Parts of the code from Stack overflow
-
-```
+The distribution of the data can be seen in @fig-figure1.
+@fig-figure1 closely resembles the expected distribution of USA household income.
+As expected in any income distribution the majority of responses fall within the average income ranges of the USA, between 20,000USD and 100,000USD [@USA].
+These factors indicate that the data set has an accurate representation of household income.
 
@@
 This data is represented using a pie chart in @fig-figure2.
-
-```{r}
-#| label: fig-figure2
-#| fig-cap: "How Closely People Follow Mr.Donald Trump from Responses in a facebook ad"
-#| warning: false
-#| message: false
-#| echo: false
-
-ggplot(cleaned_data, aes(x = "", fill = follow_trump)) +
-  geom_bar() +
-  coord_polar("y") +
-  labs(fill = "Legend") +
-  theme(axis.title = element_blank())
-
-```
+This variable faces many problems as this categorical scale is not consistent across respondents.
+To be specific we mean someone who identifies as someone who does follows Not at all closely can be following Mr.
+Donald Trump more than someone who identifies as Somewhat closely.
+This is a measurement issue within to the questions asked in the survey and all self-identifying variables in general.
+@figure2 shows the quantity of respondents in each group.
+The most common response is that they follow somewhat closely, and the other responses are relatively even.
 
 ## Ethnicity Data {#sec-race_data}
+The second question of the data that we have included in our analysis is the ethnicity of the respondents.
+This again is a categorical variable, that the individual self identifies their own ethnicity.
+The response options included Asian or Pacific Islander, White / Caucasian, Hispanic, Black or African American and other.
+@tbl-race_dist shows the percentage of respondents in each  with the overwhelming majority of responses being Caucasian at nearly 70%.
+This is actually less than the most recent estimates by the United States government which estimate over 75% of the population is Caucasian [@USA].
+The data also has an over representation of Asian and Native Americans.
+This results in an under representation of Hispanic and African American populations.
 
@@
 #| label: tbl-race_dist
-#| tbl-cap: "Percentage of each Ethnicity from Responses in a facebook ad"
+#| tbl-cap: "Percentage of each Ethnicity from Responses in the facebook ad"
 #| warning: false
@@
 
-This papers goal was to identify if lower income household voted against their own interest.
-To understand this relationship we used the variable for how closely a respondent follows Mr.
+This paper's goal was to identify if lower-income households voted against their interest.
+To understand this relationship, we used the variable for how closely a respondent follows Mr.
 Donald Trump as our measurement of subscription to Republican ideas.
@@
 Donald Trump at similar levels across all income levels.
-Specifically, we mean the percentage of individuals  follow Mr.
+Specifically, we mean the percentage of individuals following Mr.
 Donald Trump at different levels is the same no matter the income class.
-This means we can not conclude that income class impacts how closely individuals follow Mr.
-Donald Trump, and therefor, cannot conclude that different income levels subscribe to republican ideas more than the other.
+This means we cannot conclude that income class impacts how closely individuals follow Mr.
+Donald Trump, and therefore, cannot conclude that different income levels subscribe to republican ideas more than others.
 
@@
 
-To further our analysis we computed the same graph however organized by race not income @fig-figure4.
+To further our analysis, we computed the same graph however organized by race, not income @fig-figure4.
 This resulted in a similar result as race is proportional between all levels of following Mr.
 Donald Trump.
-Therefore, consistent across races at to following republican rhetoric.
-Again, this means the same percentage of people that follow Mr.
+Therefore, consistent across races to follow republican rhetoric.
+Again, this means the percentage of people who follow Mr.
 Donald Trump at different levels is the same for each race.
-Obviously, this is more difficult to conclude for minorities as their representation within the data set is so small as stated in @sec-race_data
+This is more difficult to conclude for minorities as their representation within the data set is so small as stated in @sec-race_data.
 
@@
 
-Overall, the results of this analysis were inconclusive to measure how income impacts individuals propensity to follow republican rhetoric.
-There are many reasons this could be true and as stated in the @sec-intro there are multiple schools of thought previously studies on the topic.
+Overall, the results of this analysis were inconclusive to measure how income impacts individuals' propensity to follow republican rhetoric.
+There are many reasons this could be true and as stated in the @intro there are multiple schools of thought previously studied on the topic.
+
+# Discussion {sec-disc}
+## Inconclusive – not a futile exercise 
+Our results show no evident relationship between income and Republic following.
+This result is important in of itself – the insignificant relationship suggests income does not influence an individual’s choice of presidential candidate.
+There can be many possible reasons.
+The first reason is that other factors apart from income influence this choice to a much greater extent.
+For example, a family of 5 kids may be more influenced by a candidate promising better institutional infrastructure like more schools and subsidized education.
+As mentioned in ‘Factors Influencing Voting Decision: A Comprehensive Literature Review’ [@mdpi], the main headings influencing decisions include ‘demographic factors, psychological factors, sociocultural factors and economic factors.’ Income is only one of the many economic factors, and so may have a very small influence on voting preference.
+
+## Weaknesses 
+The analysis in the paper is not perfect, with some changes that can make it much more robust.
+One of the limitations is the race question – the limitation of only the choice in the survey means individuals who part of any of those races are not included are unable to provide a data point.
+If some of these groups significantly change their voting pattern based on income, their contribution is lost.
+This is a classic case of sampling bias.
+Secondly, any values that were missing from the dataset were dropped for this paper. Just as stated previously, the contribution of those data points is lost, making our conclusions less precise. 
+Lastly, the survey collected data via an online platform, thereby leaving out opinions of individuals either not in possession of technology or not very adept at operating it such as the elderly.
+This is another sampling bias result, as it leaves out another key societal group for the analysis.
+Thirdly, the income variable only being measured as a categorical variable limited our analysis.
+Income is usually measured as a continous variable which would have allowed analysis such as regression to be used.
+
+# Appendix {-}
+## Figures
+
+```{r}
+#| label: fig-figure1
+#| fig-cap: "Distribution of Income from Responses in the facebook ad"
+#| warning: false
+#| message: false
+#| echo: false
+
+ggplot(cleaned_data, aes(x = reorder(hhld_inc, -table(hhld_inc)[hhld_inc]), fill = hhld_inc)) +
+  geom_bar() +
+  labs(x = "Household Income",
+       y = "Number of Respondents") +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
+  guides(fill = FALSE) # Parts of the code from Stack overflow
+
+```
+
+```{r}
+#| label: fig-figure2
+#| fig-cap: "How Closely People Follow Mr.Donald Trump from Responses in the facebook ad"
+#| warning: false
+#| message: false
+#| echo: false
+
+ggplot(cleaned_data, aes(x = "", fill = follow_trump)) +
+  geom_bar() +
+  coord_polar("y") +
+  labs(fill = "Legend") +
+  theme(axis.title = element_blank())
+
+```
+
+## Data Cleaning
+The data cleaning for this analysis was very straightforward.
+Once the data was obtained using the links mentioned in the paper or the github repo, the variables reqired for the analysis we compiled and any response with missing data was removed.
 

### 2024-02-15 outputs/paper/paper.tex
updates

@@
 \hypersetup{
-  pdftitle={Paper 2},
+  pdftitle={How Household Income Impacts Political Views, Focusing on Mr.~Donald Trump, Yielded Inconclusive Results},
   pdfauthor={Gavin Crooks; Samarth Rajani},
@@
 
-\title{Paper 2\thanks{Code and data are available at:
+\title{How Household Income Impacts Political Views, Focusing on
+Mr.~Donald Trump, Yielded Inconclusive Results\thanks{Code and data are
+available at:
 LINK.https://github.com/Crooksyyy/The-Effects-of-Social-Media}}
@@
 \begin{abstract}
-First sentence. Second sentence. Third sentence. Fourth sentence.
+This study explores the relationship between household income,
+ethnicity, and political preferences using data from `The Welfare
+Effects of Social Media.' Despite inconclusive findings challenging the
+presumed impact of income on political views, our innovative metric,
+measuring respondents' propensity to follow Donald Trump, did not
+provide conclusive results. This introduces new avenues in political
+science and statistics, encouraging further exploration into
+understanding the dynamics of these relationships. The study contributes
+to the ongoing discourse on the complex relationships between income,
+ethnicity, and political inclinations.
 \end{abstract}
@@
 and we intend on tackling this issue at hand of whether different income
-brackets tend to vote differently.
+brackets tend to vote differently. By measuring the difference in
+propensity to follow Mr.~Donald Trump in relation to household income.
 
 The remainder of this paper is structured as follows.
-Section~\ref{sec-data} will intorduce the data set and the variables it
+Section~\ref{sec-data} will introduce the data set and the variables it
 contains. Section~\ref{sec-results} will display the findings of our
-data in relation to our paper. Section~\ref{sec-data} focuses on the
-strength and weaknesses of our paper.
+data in relation to our paper. The \textbf{?@sec-disc} will discuss why
+the findings matter and the weaknesses of our analysis.
 
@@
 was also available, and the entries with that response were dropped. The
-distribution of the data can be seen in Figure~\ref{fig-figure1} .
-
-\begin{figure}
-
-\centering{
-
-\includegraphics{paper_files/figure-pdf/fig-figure1-1.pdf}
-
-}
-
-\caption{\label{fig-figure1}Distribution of Income from Responses in a
-facebook ad}
-
-\end{figure}%
+distribution of the data can be seen in Figure~\ref{fig-figure1}.
+Figure~\ref{fig-figure1} closely resembles the expected distribution of
+USA household income. As expected in any income distribution the
+majority of responses fall within the average income ranges of the USA,
+between 20,000USD and 100,000USD (2022). These factors indicate that the
+data set has an accurate representation of household income.
 
@@
 ideas. This data is represented using a pie chart in
-Figure~\ref{fig-figure2}.
-
-\begin{figure}
-
-\centering{
-
-\includegraphics{paper_files/figure-pdf/fig-figure2-1.pdf}
-
-}
-
-\caption{\label{fig-figure2}How Closely People Follow Mr.Donald Trump
-from Responses in a facebook ad}
-
-\end{figure}%
+Figure~\ref{fig-figure2}. This variable faces many problems as this
+categorical scale is not consistent across respondents. To be specific
+we mean someone who identifies as someone who does follows Not at all
+closely can be following Mr.~Donald Trump more than someone who
+identifies as Somewhat closely. This is a measurement issue within to
+the questions asked in the survey and all self-identifying variables in
+general. (\textbf{figure2?}) shows the quantity of respondents in each
+group. The most common response is that they follow somewhat closely,
+and the other responses are relatively even.
 
 \subsection{Ethnicity Data}\label{sec-race_data}
+
+The second question of the data that we have included in our analysis is
+the ethnicity of the respondents. This again is a categorical variable,
+that the individual self identifies their own ethnicity. The response
+options included Asian or Pacific Islander, White / Caucasian, Hispanic,
+Black or African American and other. Table~\ref{tbl-race_dist} shows the
+percentage of respondents in each with the overwhelming majority of
+responses being Caucasian at nearly 70\%. This is actually less than the
+most recent estimates by the United States government which estimate
+over 75\% of the population is Caucasian (2022). The data also has an
+over representation of Asian and Native Americans. This results in an
+under representation of Hispanic and African American populations.
 
@@
 \caption{\label{tbl-race\_dist}Percentage of each Ethnicity from
-Responses in a facebook ad}
+Responses in the facebook ad}
 
@@
 
-This papers goal was to identify if lower income household voted against
-their own interest. To understand this relationship we used the variable
-for how closely a respondent follows Mr.~Donald Trump as our measurement
-of subscription to Republican ideas. Using this measurement, we
-organized the proportion of individuals by income class to how closely
-they follow Mr.~Donald Trump in Figure~\ref{fig-figure3}. This graph
-shows that a proportional amount of each income class follows Mr.~Donald
-Trump at similar levels across all income levels. Specifically, we mean
-the percentage of individuals follow Mr.~Donald Trump at different
-levels is the same no matter the income class. This means we can not
-conclude that income class impacts how closely individuals follow
-Mr.~Donald Trump, and therefor, cannot conclude that different income
-levels subscribe to republican ideas more than the other.
+This paper's goal was to identify if lower-income households voted
+against their interest. To understand this relationship, we used the
+variable for how closely a respondent follows Mr.~Donald Trump as our
+measurement of subscription to Republican ideas. Using this measurement,
+we organized the proportion of individuals by income class to how
+closely they follow Mr.~Donald Trump in Figure~\ref{fig-figure3}. This
+graph shows that a proportional amount of each income class follows
+Mr.~Donald Trump at similar levels across all income levels.
+Specifically, we mean the percentage of individuals following Mr.~Donald
+Trump at different levels is the same no matter the income class. This
+means we cannot conclude that income class impacts how closely
+individuals follow Mr.~Donald Trump, and therefore, cannot conclude that
+different income levels subscribe to republican ideas more than others.
 
@@
 
-To further our analysis we computed the same graph however organized by
-race not income Figure~\ref{fig-figure4}. This resulted in a similar
+To further our analysis, we computed the same graph however organized by
+race, not income Figure~\ref{fig-figure4}. This resulted in a similar
 result as race is proportional between all levels of following
-Mr.~Donald Trump. Therefore, consistent across races at to following
-republican rhetoric. Again, this means the same percentage of people
-that follow Mr.~Donald Trump at different levels is the same for each
-race. Obviously, this is more difficult to conclude for minorities as
-their representation within the data set is so small as stated in
-Section~\ref{sec-race_data}
+Mr.~Donald Trump. Therefore, consistent across races to follow
+republican rhetoric. Again, this means the percentage of people who
+follow Mr.~Donald Trump at different levels is the same for each race.
+This is more difficult to conclude for minorities as their
+representation within the data set is so small as stated in
+Section~\ref{sec-race_data}.
 
@@
 Overall, the results of this analysis were inconclusive to measure how
-income impacts individuals propensity to follow republican rhetoric.
+income impacts individuals' propensity to follow republican rhetoric.
 There are many reasons this could be true and as stated in the
-Section~\ref{sec-intro} there are multiple schools of thought previously
-studies on the topic.
+(\textbf{intro?}) there are multiple schools of thought previously
+studied on the topic.
+
+\section{Discussion \{sec-disc\}}\label{discussion-sec-disc}
+
+\subsection{Inconclusive -- not a futile
+exercise}\label{inconclusive-not-a-futile-exercise}
+
+Our results show no evident relationship between income and Republic
+following. This result is important in of itself -- the insignificant
+relationship suggests income does not influence an individual's choice
+of presidential candidate. There can be many possible reasons. The first
+reason is that other factors apart from income influence this choice to
+a much greater extent. For example, a family of 5 kids may be more
+influenced by a candidate promising better institutional infrastructure
+like more schools and subsidized education. As mentioned in `Factors
+Influencing Voting Decision: A Comprehensive Literature Review'
+(Kulachai, Lerdtomornsakul, and Homyamyen 2023), the main headings
+influencing decisions include `demographic factors, psychological
+factors, sociocultural factors and economic factors.' Income is only one
+of the many economic factors, and so may have a very small influence on
+voting preference.
+
+\subsection{Weaknesses}\label{weaknesses}
+
+The analysis in the paper is not perfect, with some changes that can
+make it much more robust. One of the limitations is the race question --
+the limitation of only the choice in the survey means individuals who
+part of any of those races are not included are unable to provide a data
+point. If some of these groups significantly change their voting pattern
+based on income, their contribution is lost. This is a classic case of
+sampling bias. Secondly, any values that were missing from the dataset
+were dropped for this paper. Just as stated previously, the contribution
+of those data points is lost, making our conclusions less precise.
+Lastly, the survey collected data via an online platform, thereby
+leaving out opinions of individuals either not in possession of
+technology or not very adept at operating it such as the elderly. This
+is another sampling bias result, as it leaves out another key societal
+group for the analysis. Thirdly, the income variable only being measured
+as a categorical variable limited our analysis. Income is usually
+measured as a continous variable which would have allowed analysis such
+as regression to be used.
+
+\section*{Appendix}\label{appendix}
+\addcontentsline{toc}{section}{Appendix}
+
+\subsection{Figures}\label{figures}
+
+\begin{figure}
+
+\centering{
+
+\includegraphics{paper_files/figure-pdf/fig-figure1-1.pdf}
+
+}
+
+\caption{\label{fig-figure1}Distribution of Income from Responses in the
+facebook ad}
+
+\end{figure}%
+
+\begin{figure}
+
+\centering{
+
+\includegraphics{paper_files/figure-pdf/fig-figure2-1.pdf}
+
+}
+
+\caption{\label{fig-figure2}How Closely People Follow Mr.Donald Trump
+from Responses in the facebook ad}
+
+\end{figure}%
+
+\subsection{Data Cleaning}\label{data-cleaning}
+
+The data cleaning for this analysis was very straightforward. Once the
+data was obtained using the links mentioned in the paper or the github
+repo, the variables reqired for the analysis we compiled and any
+response with missing data was removed.
 
@@
 \begin{CSLReferences}{1}{0}
+\bibitem[\citeproctext]{ref-USA}
+2022. \emph{U.S. Census Bureau Quickfacts: United States}.
+\url{https://www.census.gov/quickfacts/fact/table/US/PST045222}.
+
 \bibitem[\citeproctext]{ref-paper}
@@
 \url{http://www.jstor.org/stable/42956457}.
+
+\bibitem[\citeproctext]{ref-mdpi}
+Kulachai, Waiphot, Unisa Lerdtomornsakul, and Patipol Homyamyen. 2023.
+{``Factors Influencing Voting Decision: A Comprehensive Literature
+Review.''} \emph{Social Sciences}.
+\url{https://doi.org/10.3390/socsci12090469}.
 

### 2024-02-15 scripts/04-model.R
cleaning repo

@@ -1,35 +1,0 @@
-#### Preamble ####
-# Purpose: Simple Regression model of following trump vy income controlled by race and politically invovled
-# Author: Gavin Crooks and Samarth Rajani
-# Date: 14 February 2024 
-# Contact: gavin.crooks@mail.utoronto.ca or samarth.rajani@mail.utoronto.ca
-# Pre-requisites: 01-download_data and 02-data_cleaning  or 00-simulate_data 
-
-
-#### Workspace setup ####
-library(tidyverse)
-
-#### Read data ####
-cleaned_data <- read_csv("outputs/data/analysis_data.csv")
-
-# Convert categorical variables to factors
-# Code found from r bloggers
-# https://www.r-bloggers.com/2020/10/hack-how-to-convert-all-character-variables-to-factors/
-cleaned_data[sapply(cleaned_data, is.character)] <- lapply(cleaned_data[sapply(cleaned_data, is.character)], 
-                                                           as.factor)
-
-sapply(cleaned_data, class)
-
-
-
-### Model data ####
-model <- lm(factor(follow_trump) ~ factor(hhld_inc), cleaned_data)
-summary(model)
-
-#### Save model ####
-saveRDS(
-  first_model,
-  file = "outputs/models/first_model.rds"
-)
-
-

### 2024-02-15 outputs/paper/paper.qmd
Final Paper updates

@@
   - Samarth Rajani
-thanks: "Code and data are available at: LINK.https://github.com/Crooksyyy/The-Effects-of-Social-Media"
+thanks: "Code is available at: LINK.https://github.com/Crooksyyy/The-Effects-of-Social-Media.
+Data is available at :LINK.https://www.aeaweb.org/articles?id=10.1257/aer.20190658&ArticleSearch%5Bwithin%5D%5Barticletitle%5D=1&ArticleSearch%5Bwithin%5D%5Barticleabstract%5D=1&ArticleSearch%5Bwithin%5D%5Bauthorlast%5D=1&ArticleSearch%5Bq%5D=&JelClass%5Bvalue%5D=I3&journal=1&page=2&per-page=21&from=j"
 date: today
@@
 
-Our data has been obtained from ‘The Welfare Effects of Social Media’ [@paper] .
+Our data has been obtained from ‘The Welfare Effects of Social Media’ [@paper]. To obtain the raw data please use thine links available in the repo or bibliography. 
 Our code is supported by the following packages [@citeR] [@tidy] [@her] [@knitr]
@@
 Notably the dataset would contain a lot of confidential information, that if released in the replication package would cause ethical problems.
-As a result, the authors included the de-identified versions of their data collected, which was used in our analysis too.
+As a result, the authors included the de-identified versions of their data collected, which was used in our analysis too.This method of data collection obtained a large amount of data, 24 000 responses, but will bring to question the quality of the data.
+All responses were self reported, imputing a form of bias as the values obtained my not be the true.
+Specifically terms used such as 'Somewhat closely' is up into interpretation.
+THis is explored with in each variable and tested using the figures below.
 
 ## Income Data {#sec-income_data}
+
+```{r}
+#| label: fig-figure1
+#| fig-cap: "Distribution of Income from Responses in the facebook ad"
+#| warning: false
+#| message: false
+#| echo: false
+
+ggplot(cleaned_data, aes(x = reorder(hhld_inc, -table(hhld_inc)[hhld_inc]), fill = hhld_inc)) +
+  geom_bar() +
+  labs(x = "Household Income",
+       y = "Number of Respondents") +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
+  guides(fill = FALSE) # Parts of the code from Stack overflow
+
+```
 
@@
 
+```{r}
+#| label: fig-figure2
+#| fig-cap: "How Closely People Follow Mr.Donald Trump from Responses in the facebook ad"
+#| warning: false
+#| message: false
+#| echo: false
+
+ggplot(cleaned_data, aes(x = "", fill = follow_trump)) +
+  geom_bar() +
+  coord_polar("y") +
+  labs(fill = "Legend") +
+  theme(axis.title = element_blank())
+
+```
+
 Another variable of use is the extent to which the subjects follow Mr.
@@
 This is a measurement issue within to the questions asked in the survey and all self-identifying variables in general.
-@figure2 shows the quantity of respondents in each group.
+@fig-figure2 shows the quantity of respondents in each group.
 The most common response is that they follow somewhat closely, and the other responses are relatively even.
@@
 Overall, the results of this analysis were inconclusive to measure how income impacts individuals' propensity to follow republican rhetoric.
-There are many reasons this could be true and as stated in the @intro there are multiple schools of thought previously studied on the topic.
+There are many reasons this could be true and as stated in the @sec-intro there are multiple schools of thought previously studied on the topic.
 
-# Discussion {sec-disc}
+# Discussion {#sec-disc}
 ## Inconclusive – not a futile exercise 
@@
 
-# Appendix {-}
-## Figures
-
-```{r}
-#| label: fig-figure1
-#| fig-cap: "Distribution of Income from Responses in the facebook ad"
-#| warning: false
-#| message: false
-#| echo: false
-
-ggplot(cleaned_data, aes(x = reorder(hhld_inc, -table(hhld_inc)[hhld_inc]), fill = hhld_inc)) +
-  geom_bar() +
-  labs(x = "Household Income",
-       y = "Number of Respondents") +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
-  guides(fill = FALSE) # Parts of the code from Stack overflow
-
-```
-
-```{r}
-#| label: fig-figure2
-#| fig-cap: "How Closely People Follow Mr.Donald Trump from Responses in the facebook ad"
-#| warning: false
-#| message: false
-#| echo: false
-
-ggplot(cleaned_data, aes(x = "", fill = follow_trump)) +
-  geom_bar() +
-  coord_polar("y") +
-  labs(fill = "Legend") +
-  theme(axis.title = element_blank())
-
-```
+# Appendix {#sec-appendix}
 
